---
output: html_document
editor_options: 
  chunk_output_type: console
---

# AEMET data {#sec-aemet}

Load packages:

```{r}
pacman::p_load(
      here,      # file locator
      tidyverse, # data management and ggplot2 graphics
      skimr,     # get overview of data
      janitor,   # produce and adorn tabulations and cross-tabulations
      tsibble,   # manage time series
      imputeTS,  # impute NAs for time series
      jsonlite   # read json files
)
```

Data is available in the Spanish State Meteorological Agency through its opendata platform [link](https://opendata.aemet.es/centrodedescargas/productosAEMET?).

AEMET OpenData is a REST API (Application Programming Interface. REpresentational State Transfer) through which data can be downloaded free of charge.

AEMET OpenData allows two types of access where both allow access to the same data catalog and data download in reusable formats:

-   General Access: It is a graphical access, intended for the general public. Its purpose is to allow access to data for users in a friendly way. The interaction with the data is characterized by being punctual, carried out through friendly interfaces intended for a human, directed step by step and through the choice of different options.

-   AEMET OpenData API: it allows another type of interaction with the data: this interaction is characterized by the possibility of being periodic and even programmed, from any programming language, without friendly interfaces, with the possibility of self-discovery and allows information reusers to include AEMET data in their own information systems.

Last one method was used to download data from:

-   Asturias airport
-   Barcelona airport
-   Madrid airport
-   Málaga airport
-   Sevilla airport

```{r}
# List aemet raw json files
meteo_files <- list.files(
      path = here("data", "raw"),
      recursive = TRUE,
      full.names = TRUE,
      pattern = "*meteo.json"
)
```

Load and deserialize json files.

```{r}
meteo_data <- map_dfr(
      .x = meteo_files, 
      .f = ~fromJSON(.x, flatten = TRUE)
) %>% as_tibble()
meteo_data
```

All the information corresponds to airports.

```{r}
table(meteo_data$nombre)
```

Data statistics:

```{r}
skim(meteo_data)
```

Some cleaning is needed.

First of all, we will remove useless columns for further analysis and rename the others. Secondly, we will transform date to a valid format. Last but not least, we will transform numeric data to a valid numeric format.

```{r}
meteo_data <- meteo_data %>% 
      select(-indicativo, -nombre, -altitud, -horatmin, -horatmax, -horaracha, -presMax, -horaPresMax, -presMin, -horaPresMin) %>% 
      mutate(
            fecha    = as.Date(fecha, format = "%Y-%m-%d"),
            tmed     = as.numeric(sub(",", ".", tmed, fixed = TRUE)),
            prec     = as.numeric(sub(",", ".", prec, fixed = TRUE)),
            tmin     = as.numeric(sub(",", ".", tmin, fixed = TRUE)),
            tmax     = as.numeric(sub(",", ".", tmax, fixed = TRUE)),
            dir      = as.numeric(sub(",", ".", dir, fixed = TRUE)),
            velmedia = as.numeric(sub(",", ".", velmedia, fixed = TRUE)),
            racha    = as.numeric(sub(",", ".", racha, fixed = TRUE)),
            sol      = as.numeric(sub(",", ".", sol, fixed = TRUE))
      ) %>% 
      rename(
            wd     = dir,
            ws     = velmedia,
            ws_max = racha
      )
meteo_data
```

In order to unify the data with other available sources, a rename of the provinces it needed.

```{r}
meteo_data <- meteo_data %>% 
      mutate(
            provincia = case_when(
                  provincia == "ASTURIAS" ~ "Asturias",
                  provincia == "BARCELONA" ~ "Barcelona",
                  provincia == "MADRID" ~ "Madrid",
                  provincia == "MALAGA" ~ "Málaga",
                  provincia == "SEVILLA" ~ "Sevilla",
                  TRUE ~ provincia
            )
      )
unique(meteo_data$provincia)
```

The data has missing information.

```{r}
skim(meteo_data)
```

An interpolation for each provinces will be carried out in order to have the maximum information available.

## Asturias

```{r}
meteo_asturias <- meteo_data %>% 
      filter(provincia == "Asturias")
```

```{r}
# NA imputation test
imp <- na_interpolation(meteo_asturias)
```

NAs imputed to average temperature:

```{r}
ggplot_na_imputations(meteo_asturias$tmed, imp$tmed)
```

NAs imputed to precipitations:

```{r}
ggplot_na_imputations(meteo_asturias$prec, imp$prec)
```

NAs imputed to wind speed:

```{r}
ggplot_na_imputations(meteo_asturias$ws, imp$ws)
```

Data interpolation test looks good, so we proceed to charge it:

```{r}
meteo_asturias <- na_interpolation(meteo_asturias)
```

## Barcelona

```{r}
meteo_barcelona <- meteo_data %>% 
      filter(provincia == "Barcelona")
```

```{r}
# NA imputation test
imp <- na_interpolation(meteo_barcelona)
```

NAs imputed to average temperature:

```{r}
ggplot_na_imputations(meteo_barcelona$tmed, imp$tmed)
```

NAs imputed to precipitations:

```{r}
ggplot_na_imputations(meteo_barcelona$prec, imp$prec)
```

NAs imputed to wind speed:

```{r}
ggplot_na_imputations(meteo_barcelona$ws, imp$ws)
```

Data interpolation test looks good, so we proceed to charge it:

```{r}
meteo_barcelona <- na_interpolation(meteo_barcelona)
```

## Madrid

```{r}
meteo_madrid <- meteo_data %>% 
      filter(provincia == "Madrid")
```

```{r}
# NA imputation test
imp <- na_interpolation(meteo_madrid)
```

NAs imputed to average temperature:

```{r}
print("There are not NAs!")
```

NAs imputed to precipitations:

```{r}
ggplot_na_imputations(meteo_madrid$prec, imp$prec)
```

NAs imputed to wind speed:

```{r}
ggplot_na_imputations(meteo_madrid$ws, imp$ws)
```

Data interpolation test looks good, so we proceed to charge it:

```{r}
meteo_madrid <- na_interpolation(meteo_madrid)
```

## Malaga

```{r}
meteo_malaga <- meteo_data %>% 
      filter(provincia == "Málaga")
```

```{r}
# NA imputation test
imp <- na_interpolation(meteo_malaga)
```

NAs imputed to average temperature:

```{r}
ggplot_na_imputations(meteo_malaga$tmed, imp$tmed)
```

NAs imputed to precipitations:

```{r}
ggplot_na_imputations(meteo_malaga$prec, imp$prec)
```

NAs imputed to wind speed:

```{r}
print("There are not NAs!")
```

Data interpolation test looks good, so we proceed to charge it:

```{r}
meteo_malaga <- na_interpolation(meteo_malaga)
```

## Sevilla

```{r}
meteo_sevilla <- meteo_data %>% 
      filter(provincia == "Sevilla")
```

```{r}
# NA imputation test
imp <- na_interpolation(meteo_sevilla)
```

NAs imputed to average temperature:

```{r}
ggplot_na_imputations(meteo_sevilla$tmed, imp$tmed)
```

NAs imputed to precipitations:

```{r}
ggplot_na_imputations(meteo_sevilla$prec, imp$prec)
```

NAs imputed to wind speed:

```{r}
ggplot_na_imputations(meteo_sevilla$ws, imp$ws)
```

Data interpolation test looks good, so we proceed to charge it:

```{r}
meteo_sevilla <- na_interpolation(meteo_sevilla)
```

## Data combination

```{r}
meteo_data_completed <- meteo_asturias %>% 
      rbind(meteo_barcelona) %>% 
      rbind(meteo_madrid) %>% 
      rbind(meteo_malaga) %>% 
      rbind(meteo_sevilla)
unique(meteo_data_completed$provincia)
```

Final statistics:

```{r}
skim(meteo_data_completed)
```

The final data looks like:

```{r}
meteo_data_completed
```
