---
output: html_document
editor_options: 
  chunk_output_type: console
---

# CNE data {#sec-cne}

Load packages:

```{r}
# loading of packages required for the analyses
pacman::p_load(
      here,      # file locator
      tidyverse, # data management and ggplot2 graphics
      skimr      # get overview of data
)
```

Number of cases by diagnostic technique and province of residence \[[link](https://cnecovid.isciii.es/covid19/resources/metadata_tecnica_ccaa_prov_res.pdf)\]:

-   provincia_iso: ISO code of the province of residence.
-   fecha: date \[From pandemic onset to May 10, the date of symptom onset or, if not, the date of diagnosis minus 6 days. symptoms or, in the absence of symptoms, the date of diagnosis minus 6 days. From May 11, the date of symptom onset, or in the absence thereof, the date of diagnosis minus 3 days, or the date of diagnosis for cases date of diagnosis minus 3 days, or the date of diagnosis for asymptomatic cases. asymptomatic cases.
-   num_casos: Number of cases by diagnostic technique and province of residence.
-   num_casos_prueba_pcr: Number of cases with PCR laboratory test or molecular techniques.
-   num_casos_prueba_test_ac: Number of cases with laboratory test of rapid antibody test.
-   num_casos_prueba_ag: Number of cases with laboratory test of antigen detection test antigen test.
-   num_casos_prueba_elisa: Number of cases with high-resolution serology laboratory testing.
-   num_casos_prueba_desconocida: Number of cases without information on laboratory testing.

```{r}
cne_data <- read_csv(
        file = here("data", "raw", "casos_tecnica_provincia.csv")
)
```

```{r}
skim(cne_data)
```
