---
output: html_document
editor_options: 
  chunk_output_type: console
---

# GOOGLE data {#sec-google}

Load packages:

```{r}
pacman::p_load(
      here,      # file locator
      tidyverse, # data management and ggplot2 graphics
      skimr,     # get overview of data
      janitor,   # produce and adorn tabulations and cross-tabulations
      tsibble,
      imputeTS
)
```

Data is avaible in the following [link](https://www.gstatic.com/covid19/mobility/Region_Mobility_Report_CSVs.zip)

```{r}
# List local google raw files
google_files <- list.files(
      path = here("data", "raw"),
      recursive = TRUE,
      full.names = TRUE,
      pattern = "*Region_Mobility_Report.csv"
)
```

```{r}
google_data <- map_dfr(
      .x = google_files, 
      .f = ~read_csv(.x, show_col_types = FALSE)
)
google_data
```

```{r}
skim(google_data)
```

There are some discrepancies between the NA data.

sub_region_1 and iso_3166_2\_code has a total of 98,4% of completness while sub_region_2 has only 68,3%. One of the reasons could be that some sub_regions in Spain are considered both Autonomous Communities (AC)/Autonomous Cities (C) and Provinces (Pr).

For those cases, sub_region_2 contains missing values.

```{r}
# Fix sub_region_2 missing data
google_data <- google_data %>% 
      mutate(
            sub_region_2 = case_when(
                  sub_region_1 == "Asturias" ~ "Asturias",
                  sub_region_1 == "Balearic Islands" ~ "Baleares",
                  sub_region_1 == "Cantabria" ~ "Cantabria",
                  sub_region_1 == "Ceuta" ~ "Ceuta",
                  sub_region_1 == "Community of Madrid" ~ "Madrid",
                  sub_region_1 == "La Rioja" ~ "Rioja",
                  sub_region_1 == "Melilla" ~ "Melilla",
                  sub_region_1 == "Navarre" ~ "Navarra",
                  sub_region_1 == "Region of Murcia" ~ "Murcia",
                  TRUE ~ sub_region_2
            )
      )
```

```{r}
google_data %>%  
      tabyl(sub_region_1) %>% 
      adorn_pct_formatting()
```

```{r}
table(google_data$sub_region_2)
```

To clean the data, the following actions will be taken:

-   NA data from sub_region_1 and 2 will be eliminated.
-   Some columns do not add usefull information for our analysis shuch as "country_region_code", "metro_area", "census_fips_code" and "place_id". So, they will be eliminated from the dataset
-   Column names are too longer and contain redundant information. We are going to rename them.

```{r}
google_data <- google_data %>% 
      drop_na(sub_region_1, sub_region_2) %>% 
      select(-country_region, -country_region_code, -metro_area, -census_fips_code, -place_id) %>% 
      rename(
            "CA"                = sub_region_1,
            "province"          = sub_region_2,
            "fecha"             = date,
            "retail_recreation" = retail_and_recreation_percent_change_from_baseline,
            "grocery_pharmacy"  = grocery_and_pharmacy_percent_change_from_baseline,
            "parks"             = parks_percent_change_from_baseline,
            "transit_stations"  = transit_stations_percent_change_from_baseline,
            "workplaces"        = workplaces_percent_change_from_baseline,
            "residential"       = residential_percent_change_from_baseline
      )
google_data
```

```{r}
skim(google_data)
```

At this point, only the numeric variables contains NAs. As this information is embedded in time series, it will be possible to impute missing values.

Missing values are presented in all the provinces but mostly in Ceuta and Melilla.

```{r}
google_data %>% 
      pivot_longer(cols = 5:10, names_to = "variables") %>% 
      filter(is.na(value)) %>% 
      pull(province) %>% 
      table() %>% 
      sort(decreasing = TRUE)
```

To impute missing data, we will convert the data to time series:

```{r}
google_TimeS <- google_data %>% 
      pivot_longer(cols = 5:10, names_to = "variables") %>% 
      as_tsibble(index = fecha, key = c(variables, province))
```

Independent imputation of data. For that, we impute the missing values by separating the variables independently.

```{r}
grocery_pharmacy_data <- google_TimeS %>% 
      filter(variables == "grocery_pharmacy") %>% 
      select(-variables) %>% 
      group_by(province) %>% 
      na_kalman() %>% 
      rename("mob_grocery_pharmacy" = value)
```

```{r}
grocery_parks_data <- google_TimeS %>% 
      filter(variables == "parks") %>% 
      select(-variables) %>%
      group_by(province) %>% 
      na_kalman() %>% 
      rename("mob_parks" = value)
```

```{r}
grocery_residential_data <- google_TimeS %>% 
      filter(variables == "residential") %>% 
      select(-variables) %>%
      group_by(province) %>% 
      na_kalman() %>% 
      rename("mob_residential" = value)
```

```{r}
grocery_retail_recreation_data <- google_TimeS %>% 
      filter(variables == "retail_recreation") %>% 
      select(-variables) %>%
      group_by(province) %>% 
      na_kalman() %>% 
      rename("mob_retail_recreation" = value)
```

```{r}
grocery_transit_stations_data <- google_TimeS %>% 
      filter(variables == "transit_stations") %>% 
      select(-variables) %>%
      group_by(province) %>% 
      na_kalman() %>% 
      rename("mob_transit_stations" = value)
```

```{r}
grocery_workplaces_data <- google_TimeS %>% 
      filter(variables == "workplaces") %>% 
      select(-variables) %>%
      group_by(province) %>% 
      na_kalman() %>% 
      rename("mob_workplaces" = value)
```

Once imputed missing data, we can combine the data again

```{r}
google_TimeS_imputed <- grocery_pharmacy_data %>% 
      inner_join(grocery_parks_data, by=c("CA", "province", "iso_3166_2_code", "fecha")) %>% 
      inner_join(grocery_residential_data, by=c("CA", "province", "iso_3166_2_code", "fecha")) %>% 
      inner_join(grocery_retail_recreation_data, by=c("CA", "province", "iso_3166_2_code", "fecha")) %>% 
      inner_join(grocery_transit_stations_data, by=c("CA", "province", "iso_3166_2_code", "fecha")) %>% 
      inner_join(grocery_workplaces_data, by=c("CA", "province", "iso_3166_2_code", "fecha"))
google_TimeS_imputed
```

Apart from missing data, there are also some gaps in the data for Ceuta and Melilla.

```{r}
google_TimeS_imputed %>% 
      pivot_longer(cols = 5:10, names_to = "variables") %>% 
      as_tsibble(index = fecha, key = c(variables, province)) %>% 
      has_gaps(.full = TRUE) %>% 
      filter(.gaps == TRUE)
```

```{r}
google_gaps <- google_TimeS_imputed %>% 
      pivot_longer(cols = 5:10, names_to = "variables") %>% 
      as_tsibble(index = fecha, key = c(variables, province)) %>% 
      count_gaps(.full = TRUE)
google_gaps
```

Since in further analysis we will not use "Ceuta" or "Melilla" data, we chose to eliminate them rather than to impute the missing values.

```{r}
google_TimeS_imputed <- google_TimeS_imputed %>% 
      filter(!province %in% c("Ceuta", "Melilla"))
google_TimeS_imputed
```

```{r}
skim(google_TimeS_imputed)
```
