# Univariate prediction {.unnumbered}

Load packages:

```{r}
pacman::p_load(
      here,      # file locator
      tidyverse, # data management and ggplot2 graphics
      skimr,     # get overview of data
      janitor,   # produce and adorn tabulations and cross-tabulations
      tsibble,
      fable,
      feasts,
      fabletools,
      lubridate
)

covid_data <- readRDS(here("data", "clean", "final_covid_data.rds"))
```

# Before sixth epidemiological period

On one hand, we are going to train the model with data previous the start of the sixth wave of coronavirus (14 oct 2021).

On the other hand, we are going to train the model with data as of June 14th which is considered the beginning of the second epidemiological period in Spain. There are two reasons,

## Asturias

```{r}
data_asturias <- covid_data %>% 
      filter(provincia == "Asturias") %>% 
      filter(fecha > as.Date("2020-06-14", format = "%Y-%m-%d")) %>% 
      select(provincia, fecha, num_casos, num_hosp, tmed,mob_grocery_pharmacy, mob_parks,
             mob_residential, mob_retail_recreation, mob_transit_stations, mob_workplaces, mob_flujo) %>% 
      drop_na(-mob_flujo) %>% 
      as_tsibble(key = provincia, index = fecha)
data_asturias
```

```{r}
data_asturias_train <- data_asturias %>% 
      filter(fecha <= as.Date("2021-10-14", format = "%Y-%m-%d"))
summary(data_asturias_train$fecha)
```

```{r}
data_asturias_test <- data_asturias %>% 
      filter(fecha > as.Date("2021-10-14", format = "%Y-%m-%d"))
summary(data_asturias_test$fecha)
```

```{r}
lambda_asturias <- data_asturias %>%
      features(num_casos, features = guerrero) %>%
      pull(lambda_guerrero)

fit_model <- data_asturias_train %>%
      model(
            arima_at1 = ARIMA(box_cox(num_casos, lambda_asturias)),
            arima_at2 = ARIMA(box_cox(num_casos, lambda_asturias),
                              stepwise = FALSE, approx = FALSE),
            Snaive = SNAIVE(box_cox(num_casos, lambda_asturias))
      )

# Show and report model
fit_model
```

```{r warning=FALSE}
report(fit_model)
```

```{r}
fit_model %>% 
      pivot_longer(-provincia,
                   names_to = ".model",
                   values_to = "orders") %>% 
      left_join(glance(fit_model), by = c("provincia", ".model")) %>% 
      arrange(AICc) %>% 
      select(.model:BIC)
```

```{r}
# We use a Ljung-Box test >> large p-value, confirms residuals are similar / considered to white noise
fit_model %>% 
      select(Snaive) %>% 
      gg_tsresiduals()
```

```{r}
fit_model %>% 
      select(arima_at1) %>% 
      gg_tsresiduals()
```

```{r}
fit_model %>% 
      select(arima_at2) %>% 
      gg_tsresiduals()
```

```{r}
augment(fit_model) %>%
      features(.innov, ljung_box, lag=7)
```

```{r}
augment(fit_model) %>%
      features(.innov, ljung_box, lag=14)
```

```{r}
augment(fit_model) %>%
      features(.innov, ljung_box, lag=21)
```

```{r}
augment(fit_model) %>%
      features(.innov, ljung_box, lag=90)
```

```{r}
# Significant spikes out of 30 is still consistent with white noise
# To be sure, use a Ljung-Box test, which has a large p-value, confirming that
# the residuals are similar to white noise.
# Note that the alternative models also passed this test.
# 
# Forecast
fc_h7  <- fabletools::forecast(fit_model, h = 7)
fc_h14 <- fabletools::forecast(fit_model, h = 14)
fc_h21 <- fabletools::forecast(fit_model, h = 21)
fc_h90 <- fabletools::forecast(fit_model, h = 90)
```

### 7 days

```{r}
# Plots
fc_h7 %>%
      autoplot(
            data_asturias_test %>% 
                  filter(fecha <= as.Date("2021-10-14", format = "%Y-%m-%d")+days(9))
      ) +
      labs(y = "Nº cases", title = "Asturias - forecast h7")
```

```{r}
fc_h7 %>%
      autoplot(
            data_asturias %>% 
                  filter(fecha <= as.Date("2021-10-14", format = "%Y-%m-%d")+days(9) &
                               fecha > as.Date("2021-07-01", format = "%Y-%m-%d"))
      ) +
      labs(y = "Nº cases", title = "Asturias - forecast h7")
```

```{r}
# Accuracy
fabletools::accuracy(fc_h7, data_asturias)
```

### 14 days

```{r}
# Plots
fc_h14 %>%
      autoplot(
            data_asturias_test %>% 
                  filter(fecha <= as.Date("2021-10-14", format = "%Y-%m-%d")+days(16))
      ) +
      labs(y = "Nº cases", title = "Asturias - forecast h14")
```

```{r}
fc_h14 %>%
      autoplot(
            data_asturias %>% 
                  filter(fecha <= as.Date("2021-10-14", format = "%Y-%m-%d")+days(16) &
                               fecha > as.Date("2021-07-01", format = "%Y-%m-%d"))
      ) +
      labs(y = "Nº cases", title = "Asturias - forecast h14")
```

```{r}
# Accuracy
fabletools::accuracy(fc_h14, data_asturias)
```

### 21 days

```{r}
# Plots
fc_h21 %>%
      autoplot(
            data_asturias_test %>% 
                  filter(fecha <= as.Date("2021-10-14", format = "%Y-%m-%d")+days(23))
      ) +
      labs(y = "Nº cases", title = "Asturias - forecast h21")
```

```{r}
fc_h21 %>%
      autoplot(
            data_asturias %>% 
                  filter(fecha <= as.Date("2021-10-14", format = "%Y-%m-%d")+days(23) &
                               fecha > as.Date("2021-07-01", format = "%Y-%m-%d"))
      ) +
      labs(y = "Nº cases", title = "Asturias - forecast h21")
```

```{r}
# Accuracy
fabletools::accuracy(fc_h21, data_asturias)
```

### 90 days

```{r}
# Plots
fc_h90 %>%
      autoplot(
            data_asturias_test %>% 
                  filter(fecha <= as.Date("2021-10-14", format = "%Y-%m-%d")+days(92))
      ) +
      labs(y = "Nº cases", title = "Asturias - forecast h90")
```

```{r}
fc_h90 %>%
      autoplot(
            data_asturias %>% 
                  filter(fecha <= as.Date("2021-10-14", format = "%Y-%m-%d")+days(92) &
                               fecha > as.Date("2021-07-01", format = "%Y-%m-%d"))
      ) +
      labs(y = "Nº cases", title = "Asturias - forecast h90")
```

```{r}
# Accuracy
fabletools::accuracy(fc_h90, data_asturias)
```

## Barcelona

```{r}
data_barcelona <- covid_data %>% 
      filter(provincia == "Barcelona") %>% 
      filter(fecha > as.Date("2020-06-14", format = "%Y-%m-%d")) %>% 
      select(provincia, fecha, num_casos, num_hosp, tmed,mob_grocery_pharmacy, mob_parks,
             mob_residential, mob_retail_recreation, mob_transit_stations, mob_workplaces, mob_flujo) %>% 
      drop_na(-mob_flujo) %>% 
      as_tsibble(key = provincia, index = fecha)
data_barcelona
```

```{r}
data_barcelona_train <- data_barcelona %>% 
      filter(fecha <= as.Date("2021-10-14", format = "%Y-%m-%d"))
summary(data_barcelona_train$fecha)
```

```{r}
data_barcelona_test <- data_barcelona %>% 
      filter(fecha > as.Date("2021-10-14", format = "%Y-%m-%d"))
summary(data_barcelona_test$fecha)
```

```{r}
lambda_Barcelona <- data_barcelona %>%
      features(num_casos, features = guerrero) %>%
      pull(lambda_guerrero)

fit_model <- data_barcelona_train %>%
      model(
            arima_at1 = ARIMA(box_cox(num_casos, lambda_Barcelona)),
            arima_at2 = ARIMA(box_cox(num_casos, lambda_Barcelona),
                              stepwise = FALSE, approx = FALSE),
            Snaive = SNAIVE(box_cox(num_casos, lambda_Barcelona))
      )

# Show and report model
fit_model
```

```{r warning=FALSE}
report(fit_model)
```

```{r}
fit_model %>% 
      pivot_longer(-provincia,
                   names_to = ".model",
                   values_to = "orders") %>% 
      left_join(glance(fit_model), by = c("provincia", ".model")) %>% 
      arrange(AICc) %>% 
      select(.model:BIC)
```

```{r}
# We use a Ljung-Box test >> large p-value, confirms residuals are similar / considered to white noise
fit_model %>% 
      select(Snaive) %>% 
      gg_tsresiduals()
```

```{r}
fit_model %>% 
      select(arima_at1) %>% 
      gg_tsresiduals()
```

```{r}
fit_model %>% 
      select(arima_at2) %>% 
      gg_tsresiduals()
```

```{r}
augment(fit_model) %>%
      features(.innov, ljung_box, lag=7)
```

```{r}
augment(fit_model) %>%
      features(.innov, ljung_box, lag=14)
```

```{r}
augment(fit_model) %>%
      features(.innov, ljung_box, lag=21)
```

```{r}
augment(fit_model) %>%
      features(.innov, ljung_box, lag=90)
```

```{r}
# Significant spikes out of 30 is still consistent with white noise
# To be sure, use a Ljung-Box test, which has a large p-value, confirming that
# the residuals are similar to white noise.
# Note that the alternative models also passed this test.
# 
# Forecast
fc_h7  <- fabletools::forecast(fit_model, h = 7)
fc_h14 <- fabletools::forecast(fit_model, h = 14)
fc_h21 <- fabletools::forecast(fit_model, h = 21)
fc_h90 <- fabletools::forecast(fit_model, h = 90)
```

### 7 days

```{r}
# Plots
fc_h7 %>%
      autoplot(
            data_barcelona_test %>% 
                  filter(fecha <= as.Date("2021-10-14", format = "%Y-%m-%d")+days(9))
      ) +
      labs(y = "Nº cases", title = "Barcelona - forecast h7")
```

```{r}
fc_h7 %>%
      autoplot(
            data_barcelona %>% 
                  filter(fecha <= as.Date("2021-10-14", format = "%Y-%m-%d")+days(9) &
                               fecha > as.Date("2021-07-01", format = "%Y-%m-%d"))
      ) +
      labs(y = "Nº cases", title = "Barcelona - forecast h7")
```

```{r}
# Accuracy
fabletools::accuracy(fc_h7, data_barcelona)
```

### 14 days

```{r}
# Plots
fc_h14 %>%
      autoplot(
            data_barcelona_test %>% 
                  filter(fecha <= as.Date("2021-10-14", format = "%Y-%m-%d")+days(16))
      ) +
      labs(y = "Nº cases", title = "Barcelona - forecast h14")
```

```{r}
fc_h14 %>%
      autoplot(
            data_barcelona %>% 
                  filter(fecha <= as.Date("2021-10-14", format = "%Y-%m-%d")+days(16) &
                               fecha > as.Date("2021-07-01", format = "%Y-%m-%d"))
      ) +
      labs(y = "Nº cases", title = "Barcelona - forecast h14")
```

```{r}
# Accuracy
fabletools::accuracy(fc_h14, data_barcelona)
```

### 21 days

```{r}
# Plots
fc_h21 %>%
      autoplot(
            data_barcelona_test %>% 
                  filter(fecha <= as.Date("2021-10-14", format = "%Y-%m-%d")+days(23))
      ) +
      labs(y = "Nº cases", title = "Barcelona - forecast h21")
```

```{r}
fc_h21 %>%
      autoplot(
            data_barcelona %>% 
                  filter(fecha <= as.Date("2021-10-14", format = "%Y-%m-%d")+days(23) &
                               fecha > as.Date("2021-07-01", format = "%Y-%m-%d"))
      ) +
      labs(y = "Nº cases", title = "Barcelona - forecast h21")
```

```{r}
# Accuracy
fabletools::accuracy(fc_h21, data_barcelona)
```

### 90 days

```{r}
# Plots
fc_h90 %>%
      autoplot(
            data_barcelona_test %>% 
                  filter(fecha <= as.Date("2021-10-14", format = "%Y-%m-%d")+days(92))
      ) +
      labs(y = "Nº cases", title = "Barcelona - forecast h90")
```

```{r}
fc_h90 %>%
      autoplot(
            data_barcelona %>% 
                  filter(fecha <= as.Date("2021-10-14", format = "%Y-%m-%d")+days(92) &
                               fecha > as.Date("2021-07-01", format = "%Y-%m-%d"))
      ) +
      labs(y = "Nº cases", title = "Barcelona - forecast h90")
```

```{r}
# Accuracy
fabletools::accuracy(fc_h90, data_barcelona)
```

## Madrid

```{r}
data_madrid <- covid_data %>% 
      filter(provincia == "Madrid") %>% 
      filter(fecha > as.Date("2020-06-14", format = "%Y-%m-%d")) %>% 
      select(provincia, fecha, num_casos, num_hosp, tmed,mob_grocery_pharmacy, mob_parks,
             mob_residential, mob_retail_recreation, mob_transit_stations, mob_workplaces, mob_flujo) %>% 
      drop_na(-mob_flujo) %>% 
      as_tsibble(key = provincia, index = fecha)
data_madrid
```

```{r}
data_madrid_train <- data_madrid %>% 
      filter(fecha <= as.Date("2021-10-14", format = "%Y-%m-%d"))
summary(data_madrid_train$fecha)
```

```{r}
data_madrid_test <- data_madrid %>% 
      filter(fecha > as.Date("2021-10-14", format = "%Y-%m-%d"))
summary(data_madrid_test$fecha)
```

```{r}
lambda_Madrid <- data_madrid %>%
      features(num_casos, features = guerrero) %>%
      pull(lambda_guerrero)

fit_model <- data_madrid_train %>%
      model(
            arima_at1 = ARIMA(box_cox(num_casos, lambda_Madrid)),
            arima_at2 = ARIMA(box_cox(num_casos, lambda_Madrid),
                              stepwise = FALSE, approx = FALSE),
            Snaive = SNAIVE(box_cox(num_casos, lambda_Madrid))
      )

# Show and report model
fit_model
```

```{r warning=FALSE}
report(fit_model)
```

```{r}
fit_model %>% 
      pivot_longer(-provincia,
                   names_to = ".model",
                   values_to = "orders") %>% 
      left_join(glance(fit_model), by = c("provincia", ".model")) %>% 
      arrange(AICc) %>% 
      select(.model:BIC)
```

```{r}
# We use a Ljung-Box test >> large p-value, confirms residuals are similar / considered to white noise
fit_model %>% 
      select(Snaive) %>% 
      gg_tsresiduals()
```

```{r}
fit_model %>% 
      select(arima_at1) %>% 
      gg_tsresiduals()
```

```{r}
fit_model %>% 
      select(arima_at2) %>% 
      gg_tsresiduals()
```

```{r}
augment(fit_model) %>%
      features(.innov, ljung_box, lag=7)
```

```{r}
augment(fit_model) %>%
      features(.innov, ljung_box, lag=14)
```

```{r}
augment(fit_model) %>%
      features(.innov, ljung_box, lag=21)
```

```{r}
augment(fit_model) %>%
      features(.innov, ljung_box, lag=90)
```

```{r}
# Significant spikes out of 30 is still consistent with white noise
# To be sure, use a Ljung-Box test, which has a large p-value, confirming that
# the residuals are similar to white noise.
# Note that the alternative models also passed this test.
# 
# Forecast
fc_h7  <- fabletools::forecast(fit_model, h = 7)
fc_h14 <- fabletools::forecast(fit_model, h = 14)
fc_h21 <- fabletools::forecast(fit_model, h = 21)
fc_h90 <- fabletools::forecast(fit_model, h = 90)
```

### 7 days

```{r}
# Plots
fc_h7 %>%
      autoplot(
            data_madrid_test %>% 
                  filter(fecha <= as.Date("2021-10-14", format = "%Y-%m-%d")+days(9))
      ) +
      labs(y = "Nº cases", title = "Madrid - forecast h7")
```

```{r}
fc_h7 %>%
      autoplot(
            data_madrid %>% 
                  filter(fecha <= as.Date("2021-10-14", format = "%Y-%m-%d")+days(9) &
                               fecha > as.Date("2021-07-01", format = "%Y-%m-%d"))
      ) +
      labs(y = "Nº cases", title = "Madrid - forecast h7")
```

```{r}
# Accuracy
fabletools::accuracy(fc_h7, data_madrid)
```

### 14 days

```{r}
# Plots
fc_h14 %>%
      autoplot(
            data_madrid_test %>% 
                  filter(fecha <= as.Date("2021-10-14", format = "%Y-%m-%d")+days(16))
      ) +
      labs(y = "Nº cases", title = "Madrid - forecast h14")
```

```{r}
fc_h14 %>%
      autoplot(
            data_madrid %>% 
                  filter(fecha <= as.Date("2021-10-14", format = "%Y-%m-%d")+days(16) &
                               fecha > as.Date("2021-07-01", format = "%Y-%m-%d"))
      ) +
      labs(y = "Nº cases", title = "Madrid - forecast h14")
```

```{r}
# Accuracy
fabletools::accuracy(fc_h14, data_madrid)
```

### 21 days

```{r}
# Plots
fc_h21 %>%
      autoplot(
            data_madrid_test %>% 
                  filter(fecha <= as.Date("2021-10-14", format = "%Y-%m-%d")+days(23))
      ) +
      labs(y = "Nº cases", title = "Madrid - forecast h21")
```

```{r}
fc_h21 %>%
      autoplot(
            data_madrid %>% 
                  filter(fecha <= as.Date("2021-10-14", format = "%Y-%m-%d")+days(23) &
                               fecha > as.Date("2021-07-01", format = "%Y-%m-%d"))
      ) +
      labs(y = "Nº cases", title = "Madrid - forecast h21")
```

```{r}
# Accuracy
fabletools::accuracy(fc_h21, data_madrid)
```

### 90 days

```{r}
# Plots
fc_h90 %>%
      autoplot(
            data_madrid_test %>% 
                  filter(fecha <= as.Date("2021-10-14", format = "%Y-%m-%d")+days(92))
      ) +
      labs(y = "Nº cases", title = "Madrid - forecast h90")
```

```{r}
fc_h90 %>%
      autoplot(
            data_madrid %>% 
                  filter(fecha <= as.Date("2021-10-14", format = "%Y-%m-%d")+days(92) &
                               fecha > as.Date("2021-07-01", format = "%Y-%m-%d"))
      ) +
      labs(y = "Nº cases", title = "Madrid - forecast h90")
```

```{r}
# Accuracy
fabletools::accuracy(fc_h90, data_madrid)
```

## Málaga

```{r}
data_malaga <- covid_data %>% 
      filter(provincia == "Málaga") %>% 
      filter(fecha > as.Date("2020-06-14", format = "%Y-%m-%d")) %>% 
      select(provincia, fecha, num_casos, num_hosp, tmed,mob_grocery_pharmacy, mob_parks,
             mob_residential, mob_retail_recreation, mob_transit_stations, mob_workplaces, mob_flujo) %>% 
      drop_na(-mob_flujo) %>% 
      as_tsibble(key = provincia, index = fecha)
data_malaga
```

```{r}
data_malaga_train <- data_malaga %>% 
      filter(fecha <= as.Date("2021-10-14", format = "%Y-%m-%d"))
summary(data_malaga_train$fecha)
```

```{r}
data_malaga_test <- data_malaga %>% 
      filter(fecha > as.Date("2021-10-14", format = "%Y-%m-%d"))
summary(data_malaga_test$fecha)
```

```{r}
lambda_Malaga <- data_malaga %>%
      features(num_casos, features = guerrero) %>%
      pull(lambda_guerrero)

fit_model <- data_malaga_train %>%
      model(
            arima_at1 = ARIMA(box_cox(num_casos, lambda_Malaga)),
            arima_at2 = ARIMA(box_cox(num_casos, lambda_Malaga),
                              stepwise = FALSE, approx = FALSE),
            Snaive = SNAIVE(box_cox(num_casos, lambda_Malaga))
      )

# Show and report model
fit_model
```

```{r warning=FALSE}
report(fit_model)
```

```{r}
fit_model %>% 
      pivot_longer(-provincia,
                   names_to = ".model",
                   values_to = "orders") %>% 
      left_join(glance(fit_model), by = c("provincia", ".model")) %>% 
      arrange(AICc) %>% 
      select(.model:BIC)
```

```{r}
# We use a Ljung-Box test >> large p-value, confirms residuals are similar / considered to white noise
fit_model %>% 
      select(Snaive) %>% 
      gg_tsresiduals()
```

```{r}
fit_model %>% 
      select(arima_at1) %>% 
      gg_tsresiduals()
```

```{r}
fit_model %>% 
      select(arima_at2) %>% 
      gg_tsresiduals()
```

```{r}
augment(fit_model) %>%
      features(.innov, ljung_box, lag=7)
```

```{r}
augment(fit_model) %>%
      features(.innov, ljung_box, lag=14)
```

```{r}
augment(fit_model) %>%
      features(.innov, ljung_box, lag=21)
```

```{r}
augment(fit_model) %>%
      features(.innov, ljung_box, lag=90)
```

```{r}
# Significant spikes out of 30 is still consistent with white noise
# To be sure, use a Ljung-Box test, which has a large p-value, confirming that
# the residuals are similar to white noise.
# Note that the alternative models also passed this test.
# 
# Forecast
fc_h7  <- fabletools::forecast(fit_model, h = 7)
fc_h14 <- fabletools::forecast(fit_model, h = 14)
fc_h21 <- fabletools::forecast(fit_model, h = 21)
fc_h90 <- fabletools::forecast(fit_model, h = 90)
```

### 7 days

```{r}
# Plots
fc_h7 %>%
      autoplot(
            data_malaga_test %>% 
                  filter(fecha <= as.Date("2021-10-14", format = "%Y-%m-%d")+days(9))
      ) +
      labs(y = "Nº cases", title = "Malaga - forecast h7")
```

```{r}
fc_h7 %>%
      autoplot(
            data_malaga %>% 
                  filter(fecha <= as.Date("2021-10-14", format = "%Y-%m-%d")+days(9) &
                               fecha > as.Date("2021-07-01", format = "%Y-%m-%d"))
      ) +
      labs(y = "Nº cases", title = "Malaga - forecast h7")
```

```{r}
# Accuracy
fabletools::accuracy(fc_h7, data_malaga)
```

### 14 days

```{r}
# Plots
fc_h14 %>%
      autoplot(
            data_malaga_test %>% 
                  filter(fecha <= as.Date("2021-10-14", format = "%Y-%m-%d")+days(16))
      ) +
      labs(y = "Nº cases", title = "Malaga - forecast h14")
```

```{r}
fc_h14 %>%
      autoplot(
            data_malaga %>% 
                  filter(fecha <= as.Date("2021-10-14", format = "%Y-%m-%d")+days(16) &
                               fecha > as.Date("2021-07-01", format = "%Y-%m-%d"))
      ) +
      labs(y = "Nº cases", title = "Malaga - forecast h14")
```

```{r}
# Accuracy
fabletools::accuracy(fc_h14, data_malaga)
```

### 21 days

```{r}
# Plots
fc_h21 %>%
      autoplot(
            data_malaga_test %>% 
                  filter(fecha <= as.Date("2021-10-14", format = "%Y-%m-%d")+days(23))
      ) +
      labs(y = "Nº cases", title = "Malaga - forecast h21")
```

```{r}
fc_h21 %>%
      autoplot(
            data_malaga %>% 
                  filter(fecha <= as.Date("2021-10-14", format = "%Y-%m-%d")+days(23) &
                               fecha > as.Date("2021-07-01", format = "%Y-%m-%d"))
      ) +
      labs(y = "Nº cases", title = "Malaga - forecast h21")
```

```{r}
# Accuracy
fabletools::accuracy(fc_h21, data_malaga)
```

### 90 days

```{r}
# Plots
fc_h90 %>%
      autoplot(
            data_malaga_test %>% 
                  filter(fecha <= as.Date("2021-10-14", format = "%Y-%m-%d")+days(92))
      ) +
      labs(y = "Nº cases", title = "Malaga - forecast h90")
```

```{r}
fc_h90 %>%
      autoplot(
            data_malaga %>% 
                  filter(fecha <= as.Date("2021-10-14", format = "%Y-%m-%d")+days(92) &
                               fecha > as.Date("2021-07-01", format = "%Y-%m-%d"))
      ) +
      labs(y = "Nº cases", title = "Malaga - forecast h90")
```

```{r}
# Accuracy
fabletools::accuracy(fc_h90, data_malaga)
```

## Sevilla

```{r}
data_sevilla <- covid_data %>% 
      filter(provincia == "Sevilla") %>% 
      filter(fecha > as.Date("2020-06-14", format = "%Y-%m-%d")) %>% 
      select(provincia, fecha, num_casos, num_hosp, tmed,mob_grocery_pharmacy, mob_parks,
             mob_residential, mob_retail_recreation, mob_transit_stations, mob_workplaces, mob_flujo) %>% 
      drop_na(-mob_flujo) %>% 
      as_tsibble(key = provincia, index = fecha)
data_sevilla
```

```{r}
data_sevilla_train <- data_sevilla %>% 
      filter(fecha <= as.Date("2021-10-14", format = "%Y-%m-%d"))
summary(data_sevilla_train$fecha)
```

```{r}
data_sevilla_test <- data_sevilla %>% 
      filter(fecha > as.Date("2021-10-14", format = "%Y-%m-%d"))
summary(data_sevilla_test$fecha)
```

```{r}
lambda_Sevilla <- data_sevilla %>%
      features(num_casos, features = guerrero) %>%
      pull(lambda_guerrero)

fit_model <- data_sevilla_train %>%
      model(
            arima_at1 = ARIMA(box_cox(num_casos, lambda_Sevilla)),
            arima_at2 = ARIMA(box_cox(num_casos, lambda_Sevilla),
                              stepwise = FALSE, approx = FALSE),
            Snaive = SNAIVE(box_cox(num_casos, lambda_Sevilla))
      )

# Show and report model
fit_model
```

```{r warning=FALSE}
report(fit_model)
```

```{r}
fit_model %>% 
      pivot_longer(-provincia,
                   names_to = ".model",
                   values_to = "orders") %>% 
      left_join(glance(fit_model), by = c("provincia", ".model")) %>% 
      arrange(AICc) %>% 
      select(.model:BIC)
```

```{r}
# We use a Ljung-Box test >> large p-value, confirms residuals are similar / considered to white noise
fit_model %>% 
      select(Snaive) %>% 
      gg_tsresiduals()
```

```{r}
fit_model %>% 
      select(arima_at1) %>% 
      gg_tsresiduals()
```

```{r}
fit_model %>% 
      select(arima_at2) %>% 
      gg_tsresiduals()
```

```{r}
augment(fit_model) %>%
      features(.innov, ljung_box, lag=7)
```

```{r}
augment(fit_model) %>%
      features(.innov, ljung_box, lag=14)
```

```{r}
augment(fit_model) %>%
      features(.innov, ljung_box, lag=21)
```

```{r}
augment(fit_model) %>%
      features(.innov, ljung_box, lag=90)
```

```{r}
# Significant spikes out of 30 is still consistent with white noise
# To be sure, use a Ljung-Box test, which has a large p-value, confirming that
# the residuals are similar to white noise.
# Note that the alternative models also passed this test.
# 
# Forecast
fc_h7  <- fabletools::forecast(fit_model, h = 7)
fc_h14 <- fabletools::forecast(fit_model, h = 14)
fc_h21 <- fabletools::forecast(fit_model, h = 21)
fc_h90 <- fabletools::forecast(fit_model, h = 90)
```

### 7 days

```{r}
# Plots
fc_h7 %>%
      autoplot(
            data_sevilla_test %>% 
                  filter(fecha <= as.Date("2021-10-14", format = "%Y-%m-%d")+days(9))
      ) +
      labs(y = "Nº cases", title = "Sevilla - forecast h7")
```

```{r}
fc_h7 %>%
      autoplot(
            data_sevilla %>% 
                  filter(fecha <= as.Date("2021-10-14", format = "%Y-%m-%d")+days(9) &
                               fecha > as.Date("2021-07-01", format = "%Y-%m-%d"))
      ) +
      labs(y = "Nº cases", title = "Sevilla - forecast h7")
```

```{r}
# Accuracy
fabletools::accuracy(fc_h7, data_sevilla)
```

### 14 days

```{r}
# Plots
fc_h14 %>%
      autoplot(
            data_sevilla_test %>% 
                  filter(fecha <= as.Date("2021-10-14", format = "%Y-%m-%d")+days(16))
      ) +
      labs(y = "Nº cases", title = "Sevilla - forecast h14")
```

```{r}
fc_h14 %>%
      autoplot(
            data_sevilla %>% 
                  filter(fecha <= as.Date("2021-10-14", format = "%Y-%m-%d")+days(16) &
                               fecha > as.Date("2021-07-01", format = "%Y-%m-%d"))
      ) +
      labs(y = "Nº cases", title = "Sevilla - forecast h14")
```

```{r}
# Accuracy
fabletools::accuracy(fc_h14, data_sevilla)
```

### 21 days

```{r}
# Plots
fc_h21 %>%
      autoplot(
            data_sevilla_test %>% 
                  filter(fecha <= as.Date("2021-10-14", format = "%Y-%m-%d")+days(23))
      ) +
      labs(y = "Nº cases", title = "Sevilla - forecast h21")
```

```{r}
fc_h21 %>%
      autoplot(
            data_sevilla %>% 
                  filter(fecha <= as.Date("2021-10-14", format = "%Y-%m-%d")+days(23) &
                               fecha > as.Date("2021-07-01", format = "%Y-%m-%d"))
      ) +
      labs(y = "Nº cases", title = "Sevilla - forecast h21")
```

```{r}
# Accuracy
fabletools::accuracy(fc_h21, data_sevilla)
```

### 90 days

```{r}
# Plots
fc_h90 %>%
      autoplot(
            data_sevilla_test %>% 
                  filter(fecha <= as.Date("2021-10-14", format = "%Y-%m-%d")+days(92))
      ) +
      labs(y = "Nº cases", title = "Sevilla - forecast h90")
```

```{r}
fc_h90 %>%
      autoplot(
            data_sevilla %>% 
                  filter(fecha <= as.Date("2021-10-14", format = "%Y-%m-%d")+days(92) &
                               fecha > as.Date("2021-07-01", format = "%Y-%m-%d"))
      ) +
      labs(y = "Nº cases", title = "Sevilla - forecast h90")
```

```{r}
# Accuracy
fabletools::accuracy(fc_h90, data_sevilla)
```

# End of sixth epidemiological period

We are going to keep train the model with data as of June 14th which is considered the beginning of the second epidemiological period in Spain. There are two reasons.

But, instead of predict the last wave, we are going to predict the deleration of infections as to 31 jan 2022.

## Asturias

```{r}
data_asturias <- covid_data %>% 
      filter(provincia == "Asturias") %>% 
      filter(fecha > as.Date("2020-06-14", format = "%Y-%m-%d")) %>% 
      select(provincia, fecha, num_casos, num_hosp, tmed,mob_grocery_pharmacy, mob_parks,
             mob_residential, mob_retail_recreation, mob_transit_stations, mob_workplaces, mob_flujo) %>% 
      drop_na(-mob_flujo) %>% 
      as_tsibble(key = provincia, index = fecha)
data_asturias
```

```{r}
data_asturias_train <- data_asturias %>% 
      filter(fecha <= as.Date("2022-01-31", format = "%Y-%m-%d"))
summary(data_asturias_train$fecha)
```

```{r}
data_asturias_test <- data_asturias %>% 
      filter(fecha > as.Date("2022-01-31", format = "%Y-%m-%d"))
summary(data_asturias_test$fecha)
```

```{r}
lambda_asturias <- data_asturias %>%
      features(num_casos, features = guerrero) %>%
      pull(lambda_guerrero)

fit_model <- data_asturias_train %>%
      model(
            arima_at1 = ARIMA(box_cox(num_casos, lambda_asturias)),
            arima_at2 = ARIMA(box_cox(num_casos, lambda_asturias),
                              stepwise = FALSE, approx = FALSE),
            Snaive = SNAIVE(box_cox(num_casos, lambda_asturias))
      )

# Show and report model
fit_model
```

```{r warning=FALSE}
report(fit_model)
```

```{r}
fit_model %>% 
      pivot_longer(-provincia,
                   names_to = ".model",
                   values_to = "orders") %>% 
      left_join(glance(fit_model), by = c("provincia", ".model")) %>% 
      arrange(AICc) %>% 
      select(.model:BIC)
```

```{r}
# We use a Ljung-Box test >> large p-value, confirms residuals are similar / considered to white noise
fit_model %>% 
      select(Snaive) %>% 
      gg_tsresiduals()
```

```{r}
fit_model %>% 
      select(arima_at1) %>% 
      gg_tsresiduals()
```

```{r}
fit_model %>% 
      select(arima_at2) %>% 
      gg_tsresiduals()
```

```{r}
augment(fit_model) %>%
      features(.innov, ljung_box, lag=7)
```

```{r}
augment(fit_model) %>%
      features(.innov, ljung_box, lag=14)
```

```{r}
augment(fit_model) %>%
      features(.innov, ljung_box, lag=21)
```

```{r}
augment(fit_model) %>%
      features(.innov, ljung_box, lag=90)
```

```{r}
# Significant spikes out of 30 is still consistent with white noise
# To be sure, use a Ljung-Box test, which has a large p-value, confirming that
# the residuals are similar to white noise.
# Note that the alternative models also passed this test.
# 
# Forecast
fc_h7  <- fabletools::forecast(fit_model, h = 7)
fc_h14 <- fabletools::forecast(fit_model, h = 14)
fc_h21 <- fabletools::forecast(fit_model, h = 21)
fc_h90 <- fabletools::forecast(fit_model, h = 90)
```

### 7 days

```{r}
# Plots
fc_h7 %>%
      autoplot(
            data_asturias_test %>% 
                  filter(fecha <= as.Date("2022-01-31", format = "%Y-%m-%d")+days(9))
      ) +
      labs(y = "Nº cases", title = "Asturias - forecast h7")
```

```{r}
fc_h7 %>%
      autoplot(
            data_asturias %>% 
                  filter(fecha <= as.Date("2022-01-31", format = "%Y-%m-%d")+days(9) &
                               fecha > as.Date("2021-12-01", format = "%Y-%m-%d"))
      ) +
      labs(y = "Nº cases", title = "Asturias - forecast h7")
```

```{r}
# Accuracy
fabletools::accuracy(fc_h7, data_asturias)
```

### 14 days

```{r}
# Plots
fc_h14 %>%
      autoplot(
            data_asturias_test %>% 
                  filter(fecha <= as.Date("2022-01-31", format = "%Y-%m-%d")+days(16))
      ) +
      labs(y = "Nº cases", title = "Asturias - forecast h14")
```

```{r}
fc_h14 %>%
      autoplot(
            data_asturias %>% 
                  filter(fecha <= as.Date("2022-01-31", format = "%Y-%m-%d")+days(16) &
                               fecha > as.Date("2021-12-01", format = "%Y-%m-%d"))
      ) +
      labs(y = "Nº cases", title = "Asturias - forecast h14")
```

```{r}
# Accuracy
fabletools::accuracy(fc_h14, data_asturias)
```

### 21 days

```{r}
# Plots
fc_h21 %>%
      autoplot(
            data_asturias_test %>% 
                  filter(fecha <= as.Date("2022-01-31", format = "%Y-%m-%d")+days(23))
      ) +
      labs(y = "Nº cases", title = "Asturias - forecast h21")
```

```{r}
fc_h21 %>%
      autoplot(
            data_asturias %>% 
                  filter(fecha <= as.Date("2022-01-31", format = "%Y-%m-%d")+days(23) &
                               fecha > as.Date("2021-12-01", format = "%Y-%m-%d"))
      ) +
      labs(y = "Nº cases", title = "Asturias - forecast h21")
```

```{r}
# Accuracy
fabletools::accuracy(fc_h21, data_asturias)
```

### 90 days

```{r}
# Plots
fc_h90 %>%
      autoplot(
            data_asturias_test %>% 
                  filter(fecha <= as.Date("2022-01-31", format = "%Y-%m-%d")+days(92))
      ) +
      labs(y = "Nº cases", title = "Asturias - forecast h90")
```

```{r}
fc_h90 %>%
      autoplot(
            data_asturias %>% 
                  filter(fecha <= as.Date("2022-01-31", format = "%Y-%m-%d")+days(92) &
                               fecha > as.Date("2021-12-01", format = "%Y-%m-%d"))
      ) +
      labs(y = "Nº cases", title = "Asturias - forecast h90")
```

```{r}
# Accuracy
fabletools::accuracy(fc_h90, data_asturias)
```

## Barcelona

```{r}
data_barcelona <- covid_data %>% 
      filter(provincia == "Barcelona") %>% 
      filter(fecha > as.Date("2020-06-14", format = "%Y-%m-%d")) %>% 
      select(provincia, fecha, num_casos, num_hosp, tmed,mob_grocery_pharmacy, mob_parks,
             mob_residential, mob_retail_recreation, mob_transit_stations, mob_workplaces, mob_flujo) %>% 
      drop_na(-mob_flujo) %>% 
      as_tsibble(key = provincia, index = fecha)
data_barcelona
```

```{r}
data_barcelona_train <- data_barcelona %>% 
      filter(fecha <= as.Date("2022-01-31", format = "%Y-%m-%d"))
summary(data_barcelona_train$fecha)
```

```{r}
data_barcelona_test <- data_barcelona %>% 
      filter(fecha > as.Date("2022-01-31", format = "%Y-%m-%d"))
summary(data_barcelona_test$fecha)
```

```{r}
lambda_Barcelona <- data_barcelona %>%
      features(num_casos, features = guerrero) %>%
      pull(lambda_guerrero)

fit_model <- data_barcelona_train %>%
      model(
            arima_at1 = ARIMA(box_cox(num_casos, lambda_Barcelona)),
            arima_at2 = ARIMA(box_cox(num_casos, lambda_Barcelona),
                              stepwise = FALSE, approx = FALSE),
            Snaive = SNAIVE(box_cox(num_casos, lambda_Barcelona))
      )

# Show and report model
fit_model
```

```{r warning=FALSE}
report(fit_model)
```

```{r}
fit_model %>% 
      pivot_longer(-provincia,
                   names_to = ".model",
                   values_to = "orders") %>% 
      left_join(glance(fit_model), by = c("provincia", ".model")) %>% 
      arrange(AICc) %>% 
      select(.model:BIC)
```

```{r}
# We use a Ljung-Box test >> large p-value, confirms residuals are similar / considered to white noise
fit_model %>% 
      select(Snaive) %>% 
      gg_tsresiduals()
```

```{r}
fit_model %>% 
      select(arima_at1) %>% 
      gg_tsresiduals()
```

```{r}
fit_model %>% 
      select(arima_at2) %>% 
      gg_tsresiduals()
```

```{r}
augment(fit_model) %>%
      features(.innov, ljung_box, lag=7)
```

```{r}
augment(fit_model) %>%
      features(.innov, ljung_box, lag=14)
```

```{r}
augment(fit_model) %>%
      features(.innov, ljung_box, lag=21)
```

```{r}
augment(fit_model) %>%
      features(.innov, ljung_box, lag=90)
```

```{r}
# Significant spikes out of 30 is still consistent with white noise
# To be sure, use a Ljung-Box test, which has a large p-value, confirming that
# the residuals are similar to white noise.
# Note that the alternative models also passed this test.
# 
# Forecast
fc_h7  <- fabletools::forecast(fit_model, h = 7)
fc_h14 <- fabletools::forecast(fit_model, h = 14)
fc_h21 <- fabletools::forecast(fit_model, h = 21)
fc_h90 <- fabletools::forecast(fit_model, h = 90)
```

### 7 days

```{r}
# Plots
fc_h7 %>%
      autoplot(
            data_barcelona_test %>% 
                  filter(fecha <= as.Date("2022-01-31", format = "%Y-%m-%d")+days(9))
      ) +
      labs(y = "Nº cases", title = "Barcelona - forecast h7")
```

```{r}
fc_h7 %>%
      autoplot(
            data_barcelona %>% 
                  filter(fecha <= as.Date("2022-01-31", format = "%Y-%m-%d")+days(9) &
                               fecha > as.Date("2021-12-01", format = "%Y-%m-%d"))
      ) +
      labs(y = "Nº cases", title = "Barcelona - forecast h7")
```

```{r}
# Accuracy
fabletools::accuracy(fc_h7, data_barcelona)
```

### 14 days

```{r}
# Plots
fc_h14 %>%
      autoplot(
            data_barcelona_test %>% 
                  filter(fecha <= as.Date("2022-01-31", format = "%Y-%m-%d")+days(16))
      ) +
      labs(y = "Nº cases", title = "Barcelona - forecast h14")
```

```{r}
fc_h14 %>%
      autoplot(
            data_barcelona %>% 
                  filter(fecha <= as.Date("2022-01-31", format = "%Y-%m-%d")+days(16) &
                               fecha > as.Date("2021-12-01", format = "%Y-%m-%d"))
      ) +
      labs(y = "Nº cases", title = "Barcelona - forecast h14")
```

```{r}
# Accuracy
fabletools::accuracy(fc_h14, data_barcelona)
```

### 21 days

```{r}
# Plots
fc_h21 %>%
      autoplot(
            data_barcelona_test %>% 
                  filter(fecha <= as.Date("2022-01-31", format = "%Y-%m-%d")+days(23))
      ) +
      labs(y = "Nº cases", title = "Barcelona - forecast h21")
```

```{r}
fc_h21 %>%
      autoplot(
            data_barcelona %>% 
                  filter(fecha <= as.Date("2022-01-31", format = "%Y-%m-%d")+days(23) &
                               fecha > as.Date("2021-12-01", format = "%Y-%m-%d"))
      ) +
      labs(y = "Nº cases", title = "Barcelona - forecast h21")
```

```{r}
# Accuracy
fabletools::accuracy(fc_h21, data_barcelona)
```

### 90 days

```{r}
# Plots
fc_h90 %>%
      autoplot(
            data_barcelona_test %>% 
                  filter(fecha <= as.Date("2022-01-31", format = "%Y-%m-%d")+days(92))
      ) +
      labs(y = "Nº cases", title = "Barcelona - forecast h90")
```

```{r}
fc_h90 %>%
      autoplot(
            data_barcelona %>% 
                  filter(fecha <= as.Date("2022-01-31", format = "%Y-%m-%d")+days(92) &
                               fecha > as.Date("2021-12-01", format = "%Y-%m-%d"))
      ) +
      labs(y = "Nº cases", title = "Barcelona - forecast h90")
```

```{r}
# Accuracy
fabletools::accuracy(fc_h90, data_barcelona)
```

## Madrid

```{r}
data_madrid <- covid_data %>% 
      filter(provincia == "Madrid") %>% 
      filter(fecha > as.Date("2020-06-14", format = "%Y-%m-%d")) %>% 
      select(provincia, fecha, num_casos, num_hosp, tmed,mob_grocery_pharmacy, mob_parks,
             mob_residential, mob_retail_recreation, mob_transit_stations, mob_workplaces, mob_flujo) %>% 
      drop_na(-mob_flujo) %>% 
      as_tsibble(key = provincia, index = fecha)
data_madrid
```

```{r}
data_madrid_train <- data_madrid %>% 
      filter(fecha <= as.Date("2022-01-31", format = "%Y-%m-%d"))
summary(data_madrid_train$fecha)
```

```{r}
data_madrid_test <- data_madrid %>% 
      filter(fecha > as.Date("2022-01-31", format = "%Y-%m-%d"))
summary(data_madrid_test$fecha)
```

```{r}
lambda_Madrid <- data_madrid %>%
      features(num_casos, features = guerrero) %>%
      pull(lambda_guerrero)

fit_model <- data_madrid_train %>%
      model(
            arima_at1 = ARIMA(box_cox(num_casos, lambda_Madrid)),
            arima_at2 = ARIMA(box_cox(num_casos, lambda_Madrid),
                              stepwise = FALSE, approx = FALSE),
            Snaive = SNAIVE(box_cox(num_casos, lambda_Madrid))
      )

# Show and report model
fit_model
```

```{r warning=FALSE}
report(fit_model)
```

```{r}
fit_model %>% 
      pivot_longer(-provincia,
                   names_to = ".model",
                   values_to = "orders") %>% 
      left_join(glance(fit_model), by = c("provincia", ".model")) %>% 
      arrange(AICc) %>% 
      select(.model:BIC)
```

```{r}
# We use a Ljung-Box test >> large p-value, confirms residuals are similar / considered to white noise
fit_model %>% 
      select(Snaive) %>% 
      gg_tsresiduals()
```

```{r}
fit_model %>% 
      select(arima_at1) %>% 
      gg_tsresiduals()
```

```{r}
fit_model %>% 
      select(arima_at2) %>% 
      gg_tsresiduals()
```

```{r}
augment(fit_model) %>%
      features(.innov, ljung_box, lag=7)
```

```{r}
augment(fit_model) %>%
      features(.innov, ljung_box, lag=14)
```

```{r}
augment(fit_model) %>%
      features(.innov, ljung_box, lag=21)
```

```{r}
augment(fit_model) %>%
      features(.innov, ljung_box, lag=90)
```

```{r}
# Significant spikes out of 30 is still consistent with white noise
# To be sure, use a Ljung-Box test, which has a large p-value, confirming that
# the residuals are similar to white noise.
# Note that the alternative models also passed this test.
# 
# Forecast
fc_h7  <- fabletools::forecast(fit_model, h = 7)
fc_h14 <- fabletools::forecast(fit_model, h = 14)
fc_h21 <- fabletools::forecast(fit_model, h = 21)
fc_h90 <- fabletools::forecast(fit_model, h = 90)
```

### 7 days

```{r}
# Plots
fc_h7 %>%
      autoplot(
            data_madrid_test %>% 
                  filter(fecha <= as.Date("2022-01-31", format = "%Y-%m-%d")+days(9))
      ) +
      labs(y = "Nº cases", title = "Madrid - forecast h7")
```

```{r}
fc_h7 %>%
      autoplot(
            data_madrid %>% 
                  filter(fecha <= as.Date("2022-01-31", format = "%Y-%m-%d")+days(9) &
                               fecha > as.Date("2021-12-01", format = "%Y-%m-%d"))
      ) +
      labs(y = "Nº cases", title = "Madrid - forecast h7")
```

```{r}
# Accuracy
fabletools::accuracy(fc_h7, data_madrid)
```

### 14 days

```{r}
# Plots
fc_h14 %>%
      autoplot(
            data_madrid_test %>% 
                  filter(fecha <= as.Date("2022-01-31", format = "%Y-%m-%d")+days(16))
      ) +
      labs(y = "Nº cases", title = "Madrid - forecast h14")
```

```{r}
fc_h14 %>%
      autoplot(
            data_madrid %>% 
                  filter(fecha <= as.Date("2022-01-31", format = "%Y-%m-%d")+days(16) &
                               fecha > as.Date("2021-12-01", format = "%Y-%m-%d"))
      ) +
      labs(y = "Nº cases", title = "Madrid - forecast h14")
```

```{r}
# Accuracy
fabletools::accuracy(fc_h14, data_madrid)
```

### 21 days

```{r}
# Plots
fc_h21 %>%
      autoplot(
            data_madrid_test %>% 
                  filter(fecha <= as.Date("2022-01-31", format = "%Y-%m-%d")+days(23))
      ) +
      labs(y = "Nº cases", title = "Madrid - forecast h21")
```

```{r}
fc_h21 %>%
      autoplot(
            data_madrid %>% 
                  filter(fecha <= as.Date("2022-01-31", format = "%Y-%m-%d")+days(23) &
                               fecha > as.Date("2021-12-01", format = "%Y-%m-%d"))
      ) +
      labs(y = "Nº cases", title = "Madrid - forecast h21")
```

```{r}
# Accuracy
fabletools::accuracy(fc_h21, data_madrid)
```

### 90 days

```{r}
# Plots
fc_h90 %>%
      autoplot(
            data_madrid_test %>% 
                  filter(fecha <= as.Date("2022-01-31", format = "%Y-%m-%d")+days(92))
      ) +
      labs(y = "Nº cases", title = "Madrid - forecast h90")
```

```{r}
fc_h90 %>%
      autoplot(
            data_madrid %>% 
                  filter(fecha <= as.Date("2022-01-31", format = "%Y-%m-%d")+days(92) &
                               fecha > as.Date("2021-12-01", format = "%Y-%m-%d"))
      ) +
      labs(y = "Nº cases", title = "Madrid - forecast h90")
```

```{r}
# Accuracy
fabletools::accuracy(fc_h90, data_madrid)
```

## Málaga

```{r}
data_malaga <- covid_data %>% 
      filter(provincia == "Málaga") %>% 
      filter(fecha > as.Date("2020-06-14", format = "%Y-%m-%d")) %>% 
      select(provincia, fecha, num_casos, num_hosp, tmed,mob_grocery_pharmacy, mob_parks,
             mob_residential, mob_retail_recreation, mob_transit_stations, mob_workplaces, mob_flujo) %>% 
      drop_na(-mob_flujo) %>% 
      as_tsibble(key = provincia, index = fecha)
data_malaga
```

```{r}
data_malaga_train <- data_malaga %>% 
      filter(fecha <= as.Date("2022-01-31", format = "%Y-%m-%d"))
summary(data_malaga_train$fecha)
```

```{r}
data_malaga_test <- data_malaga %>% 
      filter(fecha > as.Date("2022-01-31", format = "%Y-%m-%d"))
summary(data_malaga_test$fecha)
```

```{r}
lambda_Malaga <- data_malaga %>%
      features(num_casos, features = guerrero) %>%
      pull(lambda_guerrero)

fit_model <- data_malaga_train %>%
      model(
            arima_at1 = ARIMA(box_cox(num_casos, lambda_Malaga)),
            arima_at2 = ARIMA(box_cox(num_casos, lambda_Malaga),
                              stepwise = FALSE, approx = FALSE),
            Snaive = SNAIVE(box_cox(num_casos, lambda_Malaga))
      )

# Show and report model
fit_model
```

```{r warning=FALSE}
report(fit_model)
```

```{r}
fit_model %>% 
      pivot_longer(-provincia,
                   names_to = ".model",
                   values_to = "orders") %>% 
      left_join(glance(fit_model), by = c("provincia", ".model")) %>% 
      arrange(AICc) %>% 
      select(.model:BIC)
```

```{r}
# We use a Ljung-Box test >> large p-value, confirms residuals are similar / considered to white noise
fit_model %>% 
      select(Snaive) %>% 
      gg_tsresiduals()
```

```{r}
fit_model %>% 
      select(arima_at1) %>% 
      gg_tsresiduals()
```

```{r}
fit_model %>% 
      select(arima_at2) %>% 
      gg_tsresiduals()
```

```{r}
augment(fit_model) %>%
      features(.innov, ljung_box, lag=7)
```

```{r}
augment(fit_model) %>%
      features(.innov, ljung_box, lag=14)
```

```{r}
augment(fit_model) %>%
      features(.innov, ljung_box, lag=21)
```

```{r}
augment(fit_model) %>%
      features(.innov, ljung_box, lag=90)
```

```{r}
# Significant spikes out of 30 is still consistent with white noise
# To be sure, use a Ljung-Box test, which has a large p-value, confirming that
# the residuals are similar to white noise.
# Note that the alternative models also passed this test.
# 
# Forecast
fc_h7  <- fabletools::forecast(fit_model, h = 7)
fc_h14 <- fabletools::forecast(fit_model, h = 14)
fc_h21 <- fabletools::forecast(fit_model, h = 21)
fc_h90 <- fabletools::forecast(fit_model, h = 90)
```

### 7 days

```{r}
# Plots
fc_h7 %>%
      autoplot(
            data_malaga_test %>% 
                  filter(fecha <= as.Date("2022-01-31", format = "%Y-%m-%d")+days(9))
      ) +
      labs(y = "Nº cases", title = "Malaga - forecast h7")
```

```{r}
fc_h7 %>%
      autoplot(
            data_malaga %>% 
                  filter(fecha <= as.Date("2022-01-31", format = "%Y-%m-%d")+days(9) &
                               fecha > as.Date("2021-12-01", format = "%Y-%m-%d"))
      ) +
      labs(y = "Nº cases", title = "Malaga - forecast h7")
```

```{r}
# Accuracy
fabletools::accuracy(fc_h7, data_malaga)
```

### 14 days

```{r}
# Plots
fc_h14 %>%
      autoplot(
            data_malaga_test %>% 
                  filter(fecha <= as.Date("2022-01-31", format = "%Y-%m-%d")+days(16))
      ) +
      labs(y = "Nº cases", title = "Malaga - forecast h14")
```

```{r}
fc_h14 %>%
      autoplot(
            data_malaga %>% 
                  filter(fecha <= as.Date("2022-01-31", format = "%Y-%m-%d")+days(16) &
                               fecha > as.Date("2021-12-01", format = "%Y-%m-%d"))
      ) +
      labs(y = "Nº cases", title = "Malaga - forecast h14")
```

```{r}
# Accuracy
fabletools::accuracy(fc_h14, data_malaga)
```

### 21 days

```{r}
# Plots
fc_h21 %>%
      autoplot(
            data_malaga_test %>% 
                  filter(fecha <= as.Date("2022-01-31", format = "%Y-%m-%d")+days(23))
      ) +
      labs(y = "Nº cases", title = "Malaga - forecast h21")
```

```{r}
fc_h21 %>%
      autoplot(
            data_malaga %>% 
                  filter(fecha <= as.Date("2022-01-31", format = "%Y-%m-%d")+days(23) &
                               fecha > as.Date("2021-12-01", format = "%Y-%m-%d"))
      ) +
      labs(y = "Nº cases", title = "Malaga - forecast h21")
```

```{r}
# Accuracy
fabletools::accuracy(fc_h21, data_malaga)
```

### 90 days

```{r}
# Plots
fc_h90 %>%
      autoplot(
            data_malaga_test %>% 
                  filter(fecha <= as.Date("2022-01-31", format = "%Y-%m-%d")+days(92))
      ) +
      labs(y = "Nº cases", title = "Malaga - forecast h90")
```

```{r}
fc_h90 %>%
      autoplot(
            data_malaga %>% 
                  filter(fecha <= as.Date("2022-01-31", format = "%Y-%m-%d")+days(92) &
                               fecha > as.Date("2021-12-01", format = "%Y-%m-%d"))
      ) +
      labs(y = "Nº cases", title = "Malaga - forecast h90")
```

```{r}
# Accuracy
fabletools::accuracy(fc_h90, data_malaga)
```

## Sevilla

```{r}
data_sevilla <- covid_data %>% 
      filter(provincia == "Sevilla") %>% 
      filter(fecha > as.Date("2020-06-14", format = "%Y-%m-%d")) %>% 
      select(provincia, fecha, num_casos, num_hosp, tmed,mob_grocery_pharmacy, mob_parks,
             mob_residential, mob_retail_recreation, mob_transit_stations, mob_workplaces, mob_flujo) %>% 
      drop_na(-mob_flujo) %>% 
      as_tsibble(key = provincia, index = fecha)
data_sevilla
```

```{r}
data_sevilla_train <- data_sevilla %>% 
      filter(fecha <= as.Date("2022-01-31", format = "%Y-%m-%d"))
summary(data_sevilla_train$fecha)
```

```{r}
data_sevilla_test <- data_sevilla %>% 
      filter(fecha > as.Date("2022-01-31", format = "%Y-%m-%d"))
summary(data_sevilla_test$fecha)
```

```{r}
lambda_Sevilla <- data_sevilla %>%
      features(num_casos, features = guerrero) %>%
      pull(lambda_guerrero)

fit_model <- data_sevilla_train %>%
      model(
            arima_at1 = ARIMA(box_cox(num_casos, lambda_Sevilla)),
            arima_at2 = ARIMA(box_cox(num_casos, lambda_Sevilla),
                              stepwise = FALSE, approx = FALSE),
            Snaive = SNAIVE(box_cox(num_casos, lambda_Sevilla))
      )

# Show and report model
fit_model
```

```{r warning=FALSE}
report(fit_model)
```

```{r}
fit_model %>% 
      pivot_longer(-provincia,
                   names_to = ".model",
                   values_to = "orders") %>% 
      left_join(glance(fit_model), by = c("provincia", ".model")) %>% 
      arrange(AICc) %>% 
      select(.model:BIC)
```

```{r}
# We use a Ljung-Box test >> large p-value, confirms residuals are similar / considered to white noise
fit_model %>% 
      select(Snaive) %>% 
      gg_tsresiduals()
```

```{r}
fit_model %>% 
      select(arima_at1) %>% 
      gg_tsresiduals()
```

```{r}
fit_model %>% 
      select(arima_at2) %>% 
      gg_tsresiduals()
```

```{r}
augment(fit_model) %>%
      features(.innov, ljung_box, lag=7)
```

```{r}
augment(fit_model) %>%
      features(.innov, ljung_box, lag=14)
```

```{r}
augment(fit_model) %>%
      features(.innov, ljung_box, lag=21)
```

```{r}
augment(fit_model) %>%
      features(.innov, ljung_box, lag=90)
```

```{r}
# Significant spikes out of 30 is still consistent with white noise
# To be sure, use a Ljung-Box test, which has a large p-value, confirming that
# the residuals are similar to white noise.
# Note that the alternative models also passed this test.
# 
# Forecast
fc_h7  <- fabletools::forecast(fit_model, h = 7)
fc_h14 <- fabletools::forecast(fit_model, h = 14)
fc_h21 <- fabletools::forecast(fit_model, h = 21)
fc_h90 <- fabletools::forecast(fit_model, h = 90)
```

### 7 days

```{r}
# Plots
fc_h7 %>%
      autoplot(
            data_sevilla_test %>% 
                  filter(fecha <= as.Date("2022-01-31", format = "%Y-%m-%d")+days(9))
      ) +
      labs(y = "Nº cases", title = "Sevilla - forecast h7")
```

```{r}
fc_h7 %>%
      autoplot(
            data_sevilla %>% 
                  filter(fecha <= as.Date("2022-01-31", format = "%Y-%m-%d")+days(9) &
                               fecha > as.Date("2021-12-01", format = "%Y-%m-%d"))
      ) +
      labs(y = "Nº cases", title = "Sevilla - forecast h7")
```

```{r}
# Accuracy
fabletools::accuracy(fc_h7, data_sevilla)
```

### 14 days

```{r}
# Plots
fc_h14 %>%
      autoplot(
            data_sevilla_test %>% 
                  filter(fecha <= as.Date("2022-01-31", format = "%Y-%m-%d")+days(16))
      ) +
      labs(y = "Nº cases", title = "Sevilla - forecast h14")
```

```{r}
fc_h14 %>%
      autoplot(
            data_sevilla %>% 
                  filter(fecha <= as.Date("2022-01-31", format = "%Y-%m-%d")+days(16) &
                               fecha > as.Date("2021-12-01", format = "%Y-%m-%d"))
      ) +
      labs(y = "Nº cases", title = "Sevilla - forecast h14")
```

```{r}
# Accuracy
fabletools::accuracy(fc_h14, data_sevilla)
```

### 21 days

```{r}
# Plots
fc_h21 %>%
      autoplot(
            data_sevilla_test %>% 
                  filter(fecha <= as.Date("2022-01-31", format = "%Y-%m-%d")+days(23))
      ) +
      labs(y = "Nº cases", title = "Sevilla - forecast h21")
```

```{r}
fc_h21 %>%
      autoplot(
            data_sevilla %>% 
                  filter(fecha <= as.Date("2022-01-31", format = "%Y-%m-%d")+days(23) &
                               fecha > as.Date("2021-12-01", format = "%Y-%m-%d"))
      ) +
      labs(y = "Nº cases", title = "Sevilla - forecast h21")
```

```{r}
# Accuracy
fabletools::accuracy(fc_h21, data_sevilla)
```

### 90 days

```{r}
# Plots
fc_h90 %>%
      autoplot(
            data_sevilla_test %>% 
                  filter(fecha <= as.Date("2022-01-31", format = "%Y-%m-%d")+days(92))
      ) +
      labs(y = "Nº cases", title = "Sevilla - forecast h90")
```

```{r}
fc_h90 %>%
      autoplot(
            data_sevilla %>% 
                  filter(fecha <= as.Date("2022-01-31", format = "%Y-%m-%d")+days(92) &
                               fecha > as.Date("2021-12-01", format = "%Y-%m-%d"))
      ) +
      labs(y = "Nº cases", title = "Sevilla - forecast h90")
```

```{r}
# Accuracy
fabletools::accuracy(fc_h90, data_sevilla)
```
