---
output: html_document
editor_options: 
  chunk_output_type: console
---
# Task 4: Visual demographic analysis {.unnumbered}

## Introduction

As previously mentioned, the visual analysis will focus on the following provinces:

-   Asturias
-   Barcelona
-   Madrid
-   Málaga
-   Sevilla

First, we need to load packages and clean data generated during previous tasks:

```{r}
pacman::p_load(
      here,      # file locator
      tidyverse, # data management and ggplot2 graphics
      skimr,     # get overview of data
      janitor,   # produce and adorn tabulations and cross-tabulations
      lubridate, # manage dates
      PerformanceAnalytics,
      factoextra,
      tsibble,
      ggfortify
)

hosp_data <- readRDS(here("data", "clean", "final_hosp_data.rds"))
hosp_data
```

## Asturias

```{r}
data_asturias <- hosp_data %>% 
      filter(provincia == "Asturias") %>% 
      select(-provincia) %>% 
      as_tsibble(index = fecha, key = c(sexo, grupo_edad)) %>% 
      mutate(ola = case_when(
            fecha < as.Date("2020-06-21", format = "%Y-%m-%d") ~ "1_ola",
            fecha < as.Date("2020-12-06", format = "%Y-%m-%d") ~ "2_ola",
            fecha < as.Date("2021-03-14", format = "%Y-%m-%d") ~ "3_ola",
            fecha < as.Date("2021-06-19", format = "%Y-%m-%d") ~ "4_ola",
            fecha < as.Date("2021-10-13", format = "%Y-%m-%d") ~ "5_ola",
            TRUE ~ "6_ola",
      ))
data_asturias
```

### by wave

```{r}
data_asturias %>% 
      ggplot(aes(x=grupo_edad, y=num_casos)) + 
      geom_boxplot(aes(fill=grupo_edad)) +
      facet_grid(. ~ ola) + 
      theme(legend.position = "top") +
      labs(title="Asturias - Cases reported by wave and age",
           x ="Age group", y = "Nº of cases") +
      theme_bw()
```

```{r}
data_asturias %>% 
      ggplot(aes(x=grupo_edad, y=num_def)) + 
      geom_boxplot(aes(fill=grupo_edad)) +
      facet_grid(. ~ ola) + 
      theme(legend.position = "top") +
      labs(title="Asturias - Deaths reported by wave and age",
           x ="Age group", y = "Nº of cases") +
      theme_bw()
```

### by age group

```{r}
data_asturias %>% 
      ggplot(aes(x=ola, y=num_casos)) + 
      geom_boxplot(aes(fill=ola)) +
      facet_grid(. ~ grupo_edad) + 
      theme(legend.position = "top") +
      labs(title="Asturias - Cases reported by wave and age",
           x ="Age group", y = "Nº of cases") +
      theme_bw()
```

```{r}
data_asturias %>% 
      ggplot(aes(x=ola, y=num_def)) + 
      geom_boxplot(aes(fill=ola)) +
      facet_grid(. ~ grupo_edad) + 
      theme(legend.position = "top") +
      labs(title="Asturias - Deaths reported by wave and age",
           x ="Age group", y = "Nº of cases") +
      theme_bw()
```

```{r}
data_asturias %>% 
      ggplot(aes(x=fecha, y=num_casos)) +
      geom_line(aes(color=grupo_edad)) +
      geom_vline(xintercept = as.Date("2020-06-21", format = "%Y-%m-%d"), linetype="dashed") +
      geom_vline(xintercept = as.Date("2020-12-06", format = "%Y-%m-%d"), linetype="dashed") +
      geom_vline(xintercept = as.Date("2021-03-14", format = "%Y-%m-%d"), linetype="dashed") +
      geom_vline(xintercept = as.Date("2021-06-19", format = "%Y-%m-%d"), linetype="dashed") +
      geom_vline(xintercept = as.Date("2021-10-13", format = "%Y-%m-%d"), linetype="dashed") +
      facet_wrap(~sexo, ncol=1) +
      theme(legend.position = "top") +
      labs(title="Asturias - Cases reported by age group and wave",
           x ="Date", y = "Nº of cases") +
      theme_bw()
```

### by sex

```{r}
data_asturias %>% 
      ggplot(aes(x=ola, y=num_casos)) + 
      geom_boxplot(aes(fill=ola)) +
      facet_grid(. ~ sexo) + 
      theme(legend.position = "top") +
      labs(title="Asturias - Cases reported by sex and wave",
           x ="Age group", y = "Nº of cases") +
      theme_bw()
```

```{r}
data_asturias %>% 
      ggplot(aes(x=ola, y=num_def)) + 
      geom_boxplot(aes(fill=ola)) +
      facet_grid(. ~ sexo) + 
      theme(legend.position = "top") +
      labs(title="Asturias - Deaths reported by sex and age",
           x ="Age group", y = "Nº of cases") +
      theme_bw()

```

```{r}
data_asturias %>% 
      ggplot(aes(x=fecha, y=num_casos)) +
      geom_line(aes(color=sexo)) +
      geom_vline(xintercept = as.Date("2020-06-21", format = "%Y-%m-%d"), linetype="dashed") +
      geom_vline(xintercept = as.Date("2020-12-06", format = "%Y-%m-%d"), linetype="dashed") +
      geom_vline(xintercept = as.Date("2021-03-14", format = "%Y-%m-%d"), linetype="dashed") +
      geom_vline(xintercept = as.Date("2021-06-19", format = "%Y-%m-%d"), linetype="dashed") +
      geom_vline(xintercept = as.Date("2021-10-13", format = "%Y-%m-%d"), linetype="dashed") +
      facet_wrap(~grupo_edad, scales = "free_y", ncol=1) +
      theme(legend.position = "top") +
      labs(title="Asturias - Cases reported by sex and age group (free y axis)",
           x ="Date", y = "Nº of cases") +
      theme_bw()
```

## Barcelona

```{r}
data_Barcelona <- hosp_data %>% 
      filter(provincia == "Barcelona") %>% 
      select(-provincia) %>% 
      as_tsibble(index = fecha, key = c(sexo, grupo_edad)) %>% 
      mutate(ola = case_when(
            fecha < as.Date("2020-06-21", format = "%Y-%m-%d") ~ "1_ola",
            fecha < as.Date("2020-12-06", format = "%Y-%m-%d") ~ "2_ola",
            fecha < as.Date("2021-03-14", format = "%Y-%m-%d") ~ "3_ola",
            fecha < as.Date("2021-06-19", format = "%Y-%m-%d") ~ "4_ola",
            fecha < as.Date("2021-10-13", format = "%Y-%m-%d") ~ "5_ola",
            TRUE ~ "6_ola",
      ))
data_Barcelona
```

### by wave

```{r}
data_Barcelona %>% 
      ggplot(aes(x=grupo_edad, y=num_casos)) + 
      geom_boxplot(aes(fill=grupo_edad)) +
      facet_grid(. ~ ola) + 
      theme(legend.position = "top") +
      labs(title="Barcelona - Cases reported by wave and age",
           x ="Age group", y = "Nº of cases") +
      theme_bw()
```

```{r}
data_Barcelona %>% 
      ggplot(aes(x=grupo_edad, y=num_def)) + 
      geom_boxplot(aes(fill=grupo_edad)) +
      facet_grid(. ~ ola) + 
      theme(legend.position = "top") +
      labs(title="Barcelona - Deaths reported by wave and age",
           x ="Age group", y = "Nº of cases") +
      theme_bw()
```

### by age group

```{r}
data_Barcelona %>% 
      ggplot(aes(x=ola, y=num_casos)) + 
      geom_boxplot(aes(fill=ola)) +
      facet_grid(. ~ grupo_edad) + 
      theme(legend.position = "top") +
      labs(title="Barcelona - Cases reported by wave and age",
           x ="Age group", y = "Nº of cases") +
      theme_bw()
```

```{r}
data_Barcelona %>% 
      ggplot(aes(x=ola, y=num_def)) + 
      geom_boxplot(aes(fill=ola)) +
      facet_grid(. ~ grupo_edad) + 
      theme(legend.position = "top") +
      labs(title="Barcelona - Deaths reported by wave and age",
           x ="Age group", y = "Nº of cases") +
      theme_bw()
```

```{r}
data_Barcelona %>% 
      ggplot(aes(x=fecha, y=num_casos)) +
      geom_line(aes(color=grupo_edad)) +
      geom_vline(xintercept = as.Date("2020-06-21", format = "%Y-%m-%d"), linetype="dashed") +
      geom_vline(xintercept = as.Date("2020-12-06", format = "%Y-%m-%d"), linetype="dashed") +
      geom_vline(xintercept = as.Date("2021-03-14", format = "%Y-%m-%d"), linetype="dashed") +
      geom_vline(xintercept = as.Date("2021-06-19", format = "%Y-%m-%d"), linetype="dashed") +
      geom_vline(xintercept = as.Date("2021-10-13", format = "%Y-%m-%d"), linetype="dashed") +
      facet_wrap(~sexo, ncol=1) +
      theme(legend.position = "top") +
      labs(title="Barcelona - Cases reported by age group and wave",
           x ="Date", y = "Nº of cases") +
      theme_bw()
```

### by sex

```{r}
data_Barcelona %>% 
      ggplot(aes(x=ola, y=num_casos)) + 
      geom_boxplot(aes(fill=ola)) +
      facet_grid(. ~ sexo) + 
      theme(legend.position = "top") +
      labs(title="Barcelona - Cases reported by sex and wave",
           x ="Age group", y = "Nº of cases") +
      theme_bw()
```

```{r}
data_Barcelona %>% 
      ggplot(aes(x=ola, y=num_def)) + 
      geom_boxplot(aes(fill=ola)) +
      facet_grid(. ~ sexo) + 
      theme(legend.position = "top") +
      labs(title="Barcelona - Deaths reported by sex and age",
           x ="Age group", y = "Nº of cases") +
      theme_bw()

```

```{r}
data_Barcelona %>% 
      ggplot(aes(x=fecha, y=num_casos)) +
      geom_line(aes(color=sexo)) +
      geom_vline(xintercept = as.Date("2020-06-21", format = "%Y-%m-%d"), linetype="dashed") +
      geom_vline(xintercept = as.Date("2020-12-06", format = "%Y-%m-%d"), linetype="dashed") +
      geom_vline(xintercept = as.Date("2021-03-14", format = "%Y-%m-%d"), linetype="dashed") +
      geom_vline(xintercept = as.Date("2021-06-19", format = "%Y-%m-%d"), linetype="dashed") +
      geom_vline(xintercept = as.Date("2021-10-13", format = "%Y-%m-%d"), linetype="dashed") +
      facet_wrap(~grupo_edad, scales = "free_y", ncol=1) +
      theme(legend.position = "top") +
      labs(title="Barcelona - Cases reported by sex and age group (free y axis)",
           x ="Date", y = "Nº of cases") +
      theme_bw()
```

## Madrid

```{r}
data_Madrid <- hosp_data %>% 
      filter(provincia == "Madrid") %>% 
      select(-provincia) %>% 
      as_tsibble(index = fecha, key = c(sexo, grupo_edad)) %>% 
      mutate(ola = case_when(
            fecha < as.Date("2020-06-21", format = "%Y-%m-%d") ~ "1_ola",
            fecha < as.Date("2020-12-06", format = "%Y-%m-%d") ~ "2_ola",
            fecha < as.Date("2021-03-14", format = "%Y-%m-%d") ~ "3_ola",
            fecha < as.Date("2021-06-19", format = "%Y-%m-%d") ~ "4_ola",
            fecha < as.Date("2021-10-13", format = "%Y-%m-%d") ~ "5_ola",
            TRUE ~ "6_ola",
      ))
data_Madrid
```

### by wave

```{r}
data_Madrid %>% 
      ggplot(aes(x=grupo_edad, y=num_casos)) + 
      geom_boxplot(aes(fill=grupo_edad)) +
      facet_grid(. ~ ola) + 
      theme(legend.position = "top") +
      labs(title="Madrid - Cases reported by wave and age",
           x ="Age group", y = "Nº of cases") +
      theme_bw()
```

```{r}
data_Madrid %>% 
      ggplot(aes(x=grupo_edad, y=num_def)) + 
      geom_boxplot(aes(fill=grupo_edad)) +
      facet_grid(. ~ ola) + 
      theme(legend.position = "top") +
      labs(title="Madrid - Deaths reported by wave and age",
           x ="Age group", y = "Nº of cases") +
      theme_bw()
```

### by age group

```{r}
data_Madrid %>% 
      ggplot(aes(x=ola, y=num_casos)) + 
      geom_boxplot(aes(fill=ola)) +
      facet_grid(. ~ grupo_edad) + 
      theme(legend.position = "top") +
      labs(title="Madrid - Cases reported by wave and age",
           x ="Age group", y = "Nº of cases") +
      theme_bw()
```

```{r}
data_Madrid %>% 
      ggplot(aes(x=ola, y=num_def)) + 
      geom_boxplot(aes(fill=ola)) +
      facet_grid(. ~ grupo_edad) + 
      theme(legend.position = "top") +
      labs(title="Madrid - Deaths reported by wave and age",
           x ="Age group", y = "Nº of cases") +
      theme_bw()
```

```{r}
data_Madrid %>% 
      ggplot(aes(x=fecha, y=num_casos)) +
      geom_line(aes(color=grupo_edad)) +
      geom_vline(xintercept = as.Date("2020-06-21", format = "%Y-%m-%d"), linetype="dashed") +
      geom_vline(xintercept = as.Date("2020-12-06", format = "%Y-%m-%d"), linetype="dashed") +
      geom_vline(xintercept = as.Date("2021-03-14", format = "%Y-%m-%d"), linetype="dashed") +
      geom_vline(xintercept = as.Date("2021-06-19", format = "%Y-%m-%d"), linetype="dashed") +
      geom_vline(xintercept = as.Date("2021-10-13", format = "%Y-%m-%d"), linetype="dashed") +
      facet_wrap(~sexo, ncol=1) +
      theme(legend.position = "top") +
      labs(title="Madrid - Cases reported by age group and wave",
           x ="Date", y = "Nº of cases") +
      theme_bw()
```

### by sex

```{r}
data_Madrid %>% 
      ggplot(aes(x=ola, y=num_casos)) + 
      geom_boxplot(aes(fill=ola)) +
      facet_grid(. ~ sexo) + 
      theme(legend.position = "top") +
      labs(title="Madrid - Cases reported by sex and wave",
           x ="Age group", y = "Nº of cases") +
      theme_bw()
```

```{r}
data_Madrid %>% 
      ggplot(aes(x=ola, y=num_def)) + 
      geom_boxplot(aes(fill=ola)) +
      facet_grid(. ~ sexo) + 
      theme(legend.position = "top") +
      labs(title="Madrid - Deaths reported by sex and age",
           x ="Age group", y = "Nº of cases") +
      theme_bw()

```

```{r}
data_Madrid %>% 
      ggplot(aes(x=fecha, y=num_casos)) +
      geom_line(aes(color=sexo)) +
      geom_vline(xintercept = as.Date("2020-06-21", format = "%Y-%m-%d"), linetype="dashed") +
      geom_vline(xintercept = as.Date("2020-12-06", format = "%Y-%m-%d"), linetype="dashed") +
      geom_vline(xintercept = as.Date("2021-03-14", format = "%Y-%m-%d"), linetype="dashed") +
      geom_vline(xintercept = as.Date("2021-06-19", format = "%Y-%m-%d"), linetype="dashed") +
      geom_vline(xintercept = as.Date("2021-10-13", format = "%Y-%m-%d"), linetype="dashed") +
      facet_wrap(~grupo_edad, scales = "free_y", ncol=1) +
      theme(legend.position = "top") +
      labs(title="Madrid - Cases reported by sex and age group (free y axis)",
           x ="Date", y = "Nº of cases") +
      theme_bw()
```

## Malaga

```{r}
data_Malaga <- hosp_data %>% 
      filter(provincia == "Málaga") %>% 
      select(-provincia) %>% 
      as_tsibble(index = fecha, key = c(sexo, grupo_edad)) %>% 
      mutate(ola = case_when(
            fecha < as.Date("2020-06-21", format = "%Y-%m-%d") ~ "1_ola",
            fecha < as.Date("2020-12-06", format = "%Y-%m-%d") ~ "2_ola",
            fecha < as.Date("2021-03-14", format = "%Y-%m-%d") ~ "3_ola",
            fecha < as.Date("2021-06-19", format = "%Y-%m-%d") ~ "4_ola",
            fecha < as.Date("2021-10-13", format = "%Y-%m-%d") ~ "5_ola",
            TRUE ~ "6_ola",
      ))
data_Malaga
```

### by wave

```{r}
data_Malaga %>% 
      ggplot(aes(x=grupo_edad, y=num_casos)) + 
      geom_boxplot(aes(fill=grupo_edad)) +
      facet_grid(. ~ ola) + 
      theme(legend.position = "top") +
      labs(title="Malaga - Cases reported by wave and age",
           x ="Age group", y = "Nº of cases") +
      theme_bw()
```

```{r}
data_Malaga %>% 
      ggplot(aes(x=grupo_edad, y=num_def)) + 
      geom_boxplot(aes(fill=grupo_edad)) +
      facet_grid(. ~ ola) + 
      theme(legend.position = "top") +
      labs(title="Malaga - Deaths reported by wave and age",
           x ="Age group", y = "Nº of cases") +
      theme_bw()
```

### by age group

```{r}
data_Malaga %>% 
      ggplot(aes(x=ola, y=num_casos)) + 
      geom_boxplot(aes(fill=ola)) +
      facet_grid(. ~ grupo_edad) + 
      theme(legend.position = "top") +
      labs(title="Malaga - Cases reported by wave and age",
           x ="Age group", y = "Nº of cases") +
      theme_bw()
```

```{r}
data_Malaga %>% 
      ggplot(aes(x=ola, y=num_def)) + 
      geom_boxplot(aes(fill=ola)) +
      facet_grid(. ~ grupo_edad) + 
      theme(legend.position = "top") +
      labs(title="Malaga - Deaths reported by wave and age",
           x ="Age group", y = "Nº of cases") +
      theme_bw()
```

```{r}
data_Malaga %>% 
      ggplot(aes(x=fecha, y=num_casos)) +
      geom_line(aes(color=grupo_edad)) +
      geom_vline(xintercept = as.Date("2020-06-21", format = "%Y-%m-%d"), linetype="dashed") +
      geom_vline(xintercept = as.Date("2020-12-06", format = "%Y-%m-%d"), linetype="dashed") +
      geom_vline(xintercept = as.Date("2021-03-14", format = "%Y-%m-%d"), linetype="dashed") +
      geom_vline(xintercept = as.Date("2021-06-19", format = "%Y-%m-%d"), linetype="dashed") +
      geom_vline(xintercept = as.Date("2021-10-13", format = "%Y-%m-%d"), linetype="dashed") +
      facet_wrap(~sexo, ncol=1) +
      theme(legend.position = "top") +
      labs(title="Malaga - Cases reported by age group and wave",
           x ="Date", y = "Nº of cases") +
      theme_bw()
```

### by sex

```{r}
data_Malaga %>% 
      ggplot(aes(x=ola, y=num_casos)) + 
      geom_boxplot(aes(fill=ola)) +
      facet_grid(. ~ sexo) + 
      theme(legend.position = "top") +
      labs(title="Malaga - Cases reported by sex and wave",
           x ="Age group", y = "Nº of cases") +
      theme_bw()
```

```{r}
data_Malaga %>% 
      ggplot(aes(x=ola, y=num_def)) + 
      geom_boxplot(aes(fill=ola)) +
      facet_grid(. ~ sexo) + 
      theme(legend.position = "top") +
      labs(title="Malaga - Deaths reported by sex and age",
           x ="Age group", y = "Nº of cases") +
      theme_bw()

```

```{r}
data_Malaga %>% 
      ggplot(aes(x=fecha, y=num_casos)) +
      geom_line(aes(color=sexo)) +
      geom_vline(xintercept = as.Date("2020-06-21", format = "%Y-%m-%d"), linetype="dashed") +
      geom_vline(xintercept = as.Date("2020-12-06", format = "%Y-%m-%d"), linetype="dashed") +
      geom_vline(xintercept = as.Date("2021-03-14", format = "%Y-%m-%d"), linetype="dashed") +
      geom_vline(xintercept = as.Date("2021-06-19", format = "%Y-%m-%d"), linetype="dashed") +
      geom_vline(xintercept = as.Date("2021-10-13", format = "%Y-%m-%d"), linetype="dashed") +
      facet_wrap(~grupo_edad, scales = "free_y", ncol=1) +
      theme(legend.position = "top") +
      labs(title="Malaga - Cases reported by sex and age group (free y axis)",
           x ="Date", y = "Nº of cases") +
      theme_bw()
```

## Sevilla

```{r}
data_Sevilla <- hosp_data %>% 
      filter(provincia == "Sevilla") %>% 
      select(-provincia) %>% 
      as_tsibble(index = fecha, key = c(sexo, grupo_edad)) %>% 
      mutate(ola = case_when(
            fecha < as.Date("2020-06-21", format = "%Y-%m-%d") ~ "1_ola",
            fecha < as.Date("2020-12-06", format = "%Y-%m-%d") ~ "2_ola",
            fecha < as.Date("2021-03-14", format = "%Y-%m-%d") ~ "3_ola",
            fecha < as.Date("2021-06-19", format = "%Y-%m-%d") ~ "4_ola",
            fecha < as.Date("2021-10-13", format = "%Y-%m-%d") ~ "5_ola",
            TRUE ~ "6_ola",
      ))
data_Sevilla
```

### by wave

```{r}
data_Sevilla %>% 
      ggplot(aes(x=grupo_edad, y=num_casos)) + 
      geom_boxplot(aes(fill=grupo_edad)) +
      facet_grid(. ~ ola) + 
      theme(legend.position = "top") +
      labs(title="Sevilla - Cases reported by wave and age",
           x ="Age group", y = "Nº of cases") +
      theme_bw()
```

```{r}
data_Sevilla %>% 
      ggplot(aes(x=grupo_edad, y=num_def)) + 
      geom_boxplot(aes(fill=grupo_edad)) +
      facet_grid(. ~ ola) + 
      theme(legend.position = "top") +
      labs(title="Sevilla - Deaths reported by wave and age",
           x ="Age group", y = "Nº of cases") +
      theme_bw()
```

### by age group

```{r}
data_Sevilla %>% 
      ggplot(aes(x=ola, y=num_casos)) + 
      geom_boxplot(aes(fill=ola)) +
      facet_grid(. ~ grupo_edad) + 
      theme(legend.position = "top") +
      labs(title="Sevilla - Cases reported by wave and age",
           x ="Age group", y = "Nº of cases") +
      theme_bw()
```

```{r}
data_Sevilla %>% 
      ggplot(aes(x=ola, y=num_def)) + 
      geom_boxplot(aes(fill=ola)) +
      facet_grid(. ~ grupo_edad) + 
      theme(legend.position = "top") +
      labs(title="Sevilla - Deaths reported by wave and age",
           x ="Age group", y = "Nº of cases") +
      theme_bw()
```

```{r}
data_Sevilla %>% 
      ggplot(aes(x=fecha, y=num_casos)) +
      geom_line(aes(color=grupo_edad)) +
      geom_vline(xintercept = as.Date("2020-06-21", format = "%Y-%m-%d"), linetype="dashed") +
      geom_vline(xintercept = as.Date("2020-12-06", format = "%Y-%m-%d"), linetype="dashed") +
      geom_vline(xintercept = as.Date("2021-03-14", format = "%Y-%m-%d"), linetype="dashed") +
      geom_vline(xintercept = as.Date("2021-06-19", format = "%Y-%m-%d"), linetype="dashed") +
      geom_vline(xintercept = as.Date("2021-10-13", format = "%Y-%m-%d"), linetype="dashed") +
      facet_wrap(~sexo, ncol=1) +
      theme(legend.position = "top") +
      labs(title="Sevilla - Cases reported by age group and wave",
           x ="Date", y = "Nº of cases") +
      theme_bw()
```

### by sex

```{r}
data_Sevilla %>% 
      ggplot(aes(x=ola, y=num_casos)) + 
      geom_boxplot(aes(fill=ola)) +
      facet_grid(. ~ sexo) + 
      theme(legend.position = "top") +
      labs(title="Sevilla - Cases reported by sex and wave",
           x ="Age group", y = "Nº of cases") +
      theme_bw()
```

```{r}
data_Sevilla %>% 
      ggplot(aes(x=ola, y=num_def)) + 
      geom_boxplot(aes(fill=ola)) +
      facet_grid(. ~ sexo) + 
      theme(legend.position = "top") +
      labs(title="Sevilla - Deaths reported by sex and age",
           x ="Age group", y = "Nº of cases") +
      theme_bw()

```

```{r}
data_Sevilla %>% 
      ggplot(aes(x=fecha, y=num_casos)) +
      geom_line(aes(color=sexo)) +
      geom_vline(xintercept = as.Date("2020-06-21", format = "%Y-%m-%d"), linetype="dashed") +
      geom_vline(xintercept = as.Date("2020-12-06", format = "%Y-%m-%d"), linetype="dashed") +
      geom_vline(xintercept = as.Date("2021-03-14", format = "%Y-%m-%d"), linetype="dashed") +
      geom_vline(xintercept = as.Date("2021-06-19", format = "%Y-%m-%d"), linetype="dashed") +
      geom_vline(xintercept = as.Date("2021-10-13", format = "%Y-%m-%d"), linetype="dashed") +
      facet_wrap(~grupo_edad, scales = "free_y", ncol=1) +
      theme(legend.position = "top") +
      labs(title="Sevilla - Cases reported by sex and age group (free y axis)",
           x ="Date", y = "Nº of cases") +
      theme_bw()
```
